### 2023-09-04 paper.tex
Initial commit

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom

\usepackage{newtxtext}       % 
\usepackage{newtxmath}       % selects Times Roman as basic font

\usepackage{booktabs}       % Booktabs Table Style

\usepackage{graphicx}       % To frame graphic images
\usepackage[export]{adjustbox}

\usepackage[section]{placeins} % Forces an image to be displayed in it's section

%\usepackage{draftwatermark}

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\DeclareUnicodeCharacter{2212}{-}
\DeclareUnicodeCharacter{22C5}{-}

\begin{document}

%\SetWatermarkText{DRAFT}
%\SetWatermarkScale{1}

\title*{A new breeding crossover approach for evolutionary algorithms}
%

\titlerunning{Animal Life Cycle Algorithm (ALCA)}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{J. C. Felix-Saul, Mario García-Valdez}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{J. C. Felix-Saul \at TecNM, Tijuana Institute of Technology, Tijuana, Mexico, \email{jose.felix201@tectijuana.edu.mx}
\and Mario García-Valdez \at TecNM, Tijuana Institute of Technology, Tijuana, Mexico, \email{mario@tectijuana.edu.mx}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract*{In a previous work, we introduced a population-based, bio-inspired algorithm. The proposed algorithm is inspired by the biological animal life cycle, consisting of the stages of birth, growth, reproduction, and death. Our algorithm was initially based on the canonical Genetic Algorithm (GA), where all the individuals have a genotype (chromosome). One difference to highlight in our algorithm is that both the crossing and the mutation are executed through independent processes that randomly affect the population. This paper focuses on breeding, whereas in earlier versions of the algorithm, we used the traditional GA one-point crossover. In this paper, we propose a different alternative to the classical approach, where part of the genetic information is directly copied to each of the offsprings in the crossover operator, where this type of crossover may not perform well in continuous optimization problems. In this proposal, we use the parent's genetic information for each gene, using those values as lower and upper bounds of a range, where a random value within that range determines the new value for that gene index of the offspring. This is similar to what is used by algorithms such as Differential Evolution, where we consider our proposal as a variation of existing proposals. We expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals. In this paper, we use the benchmark functions introduced in the competition on evolutionary computation for the 2017 edition (CEC2017) to compare the traditional one-point crossover and our proposed strategy. Experimental results indicate that our proposed operator may be a good alternative for the canonical crossover.}

\abstract{In a previous work, we introduced a population-based, bio-inspired algorithm. The proposed algorithm is inspired by the biological animal life cycle, consisting of the stages of birth, growth, reproduction, and death. Our algorithm was initially based on the canonical Genetic Algorithm (GA), where all the individuals have a genotype (chromosome). One difference to highlight in our algorithm is that both the crossing and the mutation are executed through independent processes that randomly affect the population. This paper focuses on breeding, whereas in earlier versions of the algorithm, we used the traditional GA one-point crossover. In this paper, we propose a different alternative to the classical approach, where part of the genetic information is directly copied to each of the offsprings in the crossover operator, where this type of crossover may not perform well in continuous optimization problems. In this proposal, we use the parent's genetic information for each gene, using those values as lower and upper bounds of a range, where a random value within that range determines the new value for that gene index of the offspring. This is similar to what is used by algorithms such as Differential Evolution, where we consider our proposal as a variation of existing proposals. We expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals. In this paper, we use the benchmark functions introduced in the competition on evolutionary computation for the 2017 edition (CEC2017) to compare the traditional one-point crossover and our proposed strategy. Experimental results indicate that our proposed operator may be a good alternative for the canonical crossover.}

%\keywords{Distributed Bioinspired Algorithms \and Genetic Algorithms \and Cloud Computing.}

\newpage
\section{Introduction}
    \label{sec:1}

    Biologically inspired algorithms have proven to be very effective when
    solving complex optimization problems
    \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but
    the more challenging the problem, the more computing power it will require
    to solve them \cite{ontiveros2018high}. We consider the main reason it requires 
    more computing power is related to the evaluation of the fitness function, 
    which means calculating the solution to the real problem our algorithm is searching for. 
    One technique to manage this
    processing power demand is to use distributed computing
    \cite{thain2005distributed} or the cloud resources 
    \cite{garcia2013there,eshratifar2019bottlenet}. This strategy allows adaptation 
    of the required computing need according to the problem's complexity.

    Traditionally, bio-inspired algorithms are developed with a sequential
    (synchronous) perspective
    \cite{porto2018evolutionary,back1996evolutionary}, where a process must
    pause for the previous task to finish before continuing. 
    Some architectures address this issue \cite{valdez2021container,garcia2015evospace,merelo2016nodio} 
    by working on the cloud and finding solutions on distributed technologies.
    In this research, we present a distributed algorithm totally built as a 
    native cloud solution, where its processes execute asynchronously and in 
    parallel, managing the processing workload among several computers.  
    This strategy allows to elastically increase (or reduce) the
    computing power according to the nature of the challenge
    \cite{armbrust2010view}.

    In previous work, we introduced an algorithm inspired by the biological
    life-cycle of animal species \cite{Felix-Saul2022}. As in nature, population individuals grow older
    and age. In this algorithm's reproduction process, couples must match by mutual
    attraction, where sometimes individuals won't procreate offspring because of
    the mate's low appeal. As time passes, the environment kills its individuals
    either because of low fitness or age, causing occasional population extinction.

    We define extinction as a situation in which something no longer exists; in
    our case scenario, when we refer to extinction in our algorithm, it means
    the population of individuals no longer exists. When this condition
    presents itself, it is required to create a new population to continue
    evolution (restart).

    Population restart is the process in which we create a
    new set of individuals to replace the others that have already died (or
    were discarded) due to their aptitude. In a previous work \cite{Felix-Saul2022} 
    we used to generate a new random set of solutions, with the cost of losing 
    all evolution knowledge. In the state of the art, we have found other methodologies 
    that have successfully sought to solve the problem of population extinction with
    restarts \cite{hellwig2020modified, loshchilov2013cma, jansen2010aging, tendresse2001effects, mathias1998effects}.

    One contribution of this paper is to prove that it is possible to
    evolve a population of individuals, similar to a Genetic Algorithm (GA),
    using a distributed, parallel, and asynchronous methodology by algorithm
    implementation and testing.

    The main contribution of this research is to demonstrate how to improve the
    algorithm's behavior, by solving population extinction caused by nature's
    pressure in the Animal Life Cycle Algorithm with one of the most promising
    alternatives: the projection of the Elite towards the Champion. To validate
    our findings, we compare the results obtained with the latter and the
    random use of the more traditional alternatives (mutation and crossover),
    using classic benchmark functions for optimization for comparison.

    This paper is organized as follows. First, we 
    illustrate our algorithm model, the encountered problem with the occasional
    population extinction, and our proposed solution in
    section~\ref{section.proposal}, followed by our experimental configuration and
    results in section~\ref{section.experiments}, where we continue to analyze and
    describe some of our research findings in section~\ref{section.discussion}. We
    finalize by presenting some inferences based on the results of our experiments
    in section~\ref{section.conclusions}.

\section{Proposal}
    \label{section.proposal}

    In previous work, we presented an algorithm inspired by nature 
    \cite{Felix-Saul2022}, where we model our algorithm based on
    the generalization of the life cycle of animal species. Our algorithm, as
    in nature, consists of four stages \cite{read1968system}: birth, growth,
    reproduction, and death. One key concept of our idea is that combining
    those processes evolves the population. We propose to execute all these
    stages in parallel and asynchronously on a continuously evolving
    population.

    \subsection{Algorithm Model}

        This algorithm was inspired by the traditional Genetic Algorithm,
        meaning that all individuals have a genotype (chromosome) that is a
        list of values. We calculate the individual's fitness with the
        evaluation function and do crossover and mutation to the population.
        What makes our strategy different is that we don't use the concept of
        evolutionary generations. We manage our set of solutions as a whole
        that continuously evolve over time. Allowing individuals of different
        ages to breed and generate offspring, as it happens in nature. The
        crossover and mutation execute as independent processes that randomly
        affect the individuals.

        Our algorithm's goal is to mimic the animal life cycle, where at any
        given moment, new individuals are born to be part of the population and
        participate in the collective evolution. As time passes, they grow
        older and mature, suffering changes throughout their lives that we
        chose to represent as mutations. In our analysis, we considered a
        couple's attraction a fundamental factor in reproduction. We thought of
        death's work to maintain balance in the population by enforcing the
        survival of the fittest. As in life, death can happen to everyone: from
        a newborn to the elderly, where fitness will determine the individual's
        longevity. We display the general model concept in
        Figure~\ref{fig.algorithm_model}.

        \subsubsection{Birth} Birth is the first step of the population's
        evolution. For the algorithm representation, we begin with the
        generation of a randomly set of individuals.

        \subsubsection{Growth} In our algorithm representation, there is a
        direct correlation between elapsed time and the population's evolution.
        For this to be possible in our proposal, all individuals must grow
        older and change as time progresses. With each increment of age, an
        individual may improve or deteriorate. We chose to manifest this idea
        by performing a small mutation in each change.

        \subsubsection{Reproduction} In this step, we select a random pair of
        individuals and evaluate their couple's attraction, where fitness will
        be the decisive factor that impacts its value. The higher the fitness
        of the individual, the more attractive it will appear to fellow
        individuals. As a consequence of the previous concept, we can
        anticipate that not all couples will produce offspring, meaning
        reproduction will not always be successful.

        \subsubsection{Death} Death is the last step of the animal life cycle,
        as in our algorithm. We chose death as a representation of all the
        environmental challenges for survival, where its execution enforces the
        survival of the fittest. As time progresses, so does increase nature's
        level of danger. The better the individual fitness will increase its
        chances of survival.

        \begin{figure}
            \centering
            \includegraphics[width=100mm]{img/fig_algorithm_model.pdf}
            \caption{Animal Life Cycle Algorithm model.} \label{fig.algorithm_model}
            \end{figure}

    \subsection{Problem}

        In this algorithm's reproduction process, we find mating couples by mutual
        attraction, where sometimes individuals won't procreate offspring because of
        the mate's low appeal. As time passes, the environment could kill its
        individuals either because they have low fitness or age, leading to extinction,
        meaning there are no more individuals in the population left to reproduce. When
        this condition presents, if evaluations are available and termination
        conditions enable the algorithm to continue the search, it is required to
        create a new set of individuals. We illustrate the general flowchart for the
        Life-Cycle algorithm in Figure~\ref{fig.flowchart}.

        \begin{figure}
            \includegraphics[width=\textwidth]{img/fig_flowchart.pdf}
            \caption{Animal Life-Cycle Algorithm general flowchart.} \label{fig.flowchart}
            \end{figure}

    \subsection{Proposed Solution}
        % It is important to do a literature review for the following papers, there are 
        % other works that tackle similar problems or use it as a strategy. - M 
        In this article, we test various strategies to generate a new population to
        replace individuals that have already died (or were discarded) due to their
        aptitude, as happens in the life cycle. We previously used to generate a new
        random set of solutions, with the cost of losing all evolution knowledge.

        This article proposes some strategies to carry out this operation,
        where the presented distribution strategy obtained the best results. We
        propose one promising alternative to restart the population, to solve
        extinction caused by nature's pressure in the Life Cycle algorithm: the
        projection of the historically best-found candidate solutions (Elite)
        towards the best-found candidate solution (Champion).

        The strategy we describe in this paper use an elite set, that includes
        the historically best-found candidate solutions to take
        advantage of the historical evolution. Our goal is for the offspring to
        be somewhat close to the best individuals of the Elite.
        We use the golden ratio to compute the distance between new individuals in the population, making
        an improved distribution. We can consider our strategy an improvement 
        over other alternatives because of the findings of our latter experiments.

        Based on the historically best candidate
        solution and the elite set, we use the Golden Ratio (shown in
        Equation~\ref{eq.golden_ratio}) to compute the distance between new individuals
        in the population, making an improved distribution. It randomly selects a
        solution from the elite set and uses the Golden Ratio 
        \cite{nematollahi2020novel, gaikwad2021face, khesin2022golden, sym13081334, https://doi.org/10.1111/nyas.14895} 
        to compute multiple solutions against the best-found candidate.

        \begin{equation}
            \begin{matrix}\includegraphics[width=25mm]{img/eq_golden_ratio.pdf}\end{matrix}
            \label{eq.golden_ratio}
            \end{equation}

        This strategy is how we can calculate the projection of the
        historically Elite towards the Champion solution. To illustrate this
        concept, we include Figure~\ref{fig.elite_projection}, placing the
        Elite solution on the far right and the Champion solution on the left
        corner. We can observe the higher amount of new solutions progressively
        closer to the Champion.

        \begin{figure}
            \centering
            \includegraphics[width=0.65\textwidth]{img/fig_elite_projection.pdf}
            \caption{Projection of an Elite solution (found on the right) towards the Champion (at the left).} \label{fig.elite_projection}
            \end{figure}

        This process generates new solutions that will be the new population set. It
        uses the Golden Ratio to progressively approximate from an Elite solution to
        the Champion. This strategy facilitates to find apparently hidden solutions,
        having an exploitation emphasis. Figure~\ref{fig.elite_projection_swarm}
        displays the projection of five Elite solutions (on the corners) towards the
        Champion (in the center).

        \begin{figure}
            \centering
            \includegraphics[width=0.85\textwidth]{img/fig_elite_projection_swarm.pdf}
            \caption{Projection of five Elite solutions towards the Champion, results in a mini-swarm.} \label{fig.elite_projection_swarm}
            \end{figure}

        \FloatBarrier

\section{Experiments}
    \label{section.experiments}

    As a proof-of-concept, we implemented the algorithm with Docker containers,
    where we compare the results obtained with the projection of the Elite towards
    the Champion strategy and the random use of the more traditional alternatives
    (such as mutation and crossover), using classic benchmark functions for
    optimization as implemented by the DEAP (Distributed Evolutionary Algorithms in
    Python) library \cite{fortin2012deap}.

    \subsection{Experimental Setup}

        The following tables show the configuration used to execute the experiments for
        the analysis and comparison in this paper. In
        Table~\ref{tab.general_configuration}, we can find the General Configuration
        for the Animal Life Cycle Algorithm. All values from this configuration
        remained constant during all phases of the experiment runs. The following
        table, Table~\ref{tab.benchmark_fun_config}, shows the values used for the
        Classic Benchmark Functions for Optimization, where these are adjusted
        accordingly for each function.

        % Please add the following required packages to your document preamble:
        % \usepackage{booktabs}
        % To change the size of the font use \scriptsize or \tiny
        \begin{table}[]
            \scriptsize
            \centering
            \caption{Animal Life Cycle Algorithm (ALCA) General Configuration.}\label{tab.general_configuration}
            \begin{tabular}{@{}ll@{}}
            \toprule
            \multicolumn{2}{l}{\textbf{ALCA General Configuration}} \\ \midrule
            Function name & ALL \\
            Population & 500 \\
            Target error & 1.00E-08 \\
            Crossover rate & 100 \\
            Mutation rate & 7 \\
            Max age & 40 \\
            Tournament rep. & 100 \\
            Sample size & 20 \\
            Base approval & 80 \\
            Goal approval & 200 \\ \bottomrule
            \end{tabular}
            \end{table}

        \begin{table}[]
            \scriptsize
            \centering
            \caption{Classic Benchmark Functions for Optimization Configuration.}\label{tab.benchmark_fun_config}
            \begin{tabular}{@{}llllllll@{}}
            \toprule
            \multicolumn{8}{l}{\textbf{Benchmark Configuration Setup}} \\ \midrule
            Function name & Ackley & Bohachevsky & Griewank & Rastrigin & Sphere & Rosenbrock & Rosenbrock \\
            Dimensions & 5, 10 & 5, 10 & 5, 10 & 5, 10 & 5, 10 & 5 & 10 \\
            Max evaluations & 200,000 & 200,000 & 200,000 & 200,000 & 200,000 & 500,000 & 1,000,000 \\
            Max stagnation & 50,000 & 50,000 & 50,000 & 50,000 & 50,000 & 125,000 & 250,000 \\
            Target fitness & -20.0 & -12.0 & -150.0 & -80.0 & -50.0 & -3500.0 & -3500.0 \\
            Bound matrix & {[}-32, 32{]} & {[}-2, 2{]} & {[}-500, 500{]} & {[}-5, 5{]} & {[}-5, 5{]} & {[}-2, 2{]} & {[}-2, 2{]} \\ \bottomrule
            \end{tabular}
            \end{table}

        \FloatBarrier

    \subsection{Experiment Results}

        For each experiment, we ran 30 independent executions per algorithm and
        dimensions specified. We recorded the following results: best-found error average,
        standard deviation, total number of evaluations, and total elapsed time (in
        seconds). The labels used on the results of our summarized experiments tables
        are the following:

        \begin{itemize}
            \item   Error:       is the best-found error average.
            \item   St-Dev:      is the standard deviation calculated from the error. 
            \item   Evals.:      is the total number of evaluations the algorithm executed.
            \item   Time:        is the total elapsed or wall clock time, in seconds. 
        \end{itemize}

        The alternatives to restart this new population are the creation of a new set
        of candidate solutions based on either: 1. Crossing the Champion with the Elite;
        2. The mutation with uniform modification from the Elite; 3. The
        projection of the Elite towards the Champion; 4. Based on random use of the
        previous alternatives. We compared three strategies by grouping the previous
        alternatives in the following:

        \begin{itemize}
            \item   Xover Mutation:      Crossing the Champion with the Elite, and the mutation with uniform modification from the Elite.
            \item   Elite Projection:    The projection of the Elite towards the Champion. 
            \item   All Random:          Based on random use of the previous alternatives.
        \end{itemize}

        \subsubsection{Ackley Benchmark Function Experiment}

            The goal of the first experiment was to confirm that this paper’s
            proposed strategy obtained improved results over our basic
            technique, which created a new population with a random generation
            of a new set of candidate solutions. We chose Ackley as the first
            Classic Benchmark Function for Optimization to test our algorithm
            behavior, where Figure~\ref{fig.fun_ackley} shows its corresponding
            Box and Whisker chart, and we summarized the results in
            Tables~\ref{tab.fun_ackley5} and~\ref{tab.fun_ackley10} (for five 
            and ten dimensions, respectively).

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_ackley.pdf}
                \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Ackley Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_ackley5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Ackley Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 8.69E-08 & 1.36E-08 & 46,331 & 49.9 \\
                \textbf{Elite Projection} & 6.33E-08 & 2.70E-08 & 13,811 & 18.1 \\
                \textbf{All Random} & 6.78E-08 & 2.55E-08 & 30,236 & 32.8 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Ackley Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_ackley10}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Ackley Function - 10 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 9.35E-08 & 5.93E-09 & 104,842 & 111.7 \\
                \textbf{Elite Projection} & 5.11E-08 & 3.13E-08 & 16,019 & 20.1 \\
                \textbf{All Random} & 6.89E-08 & 2.75E-08 & 43,631 & 46.3 \\ \bottomrule
                \end{tabular}
                \end{table}

            \FloatBarrier

        \subsubsection{Bohachevsky Benchmark Function Experiment}

            As our second experiment to further validate and prove our
            algorithm behavior, we chose Bohachevsky Classic Benchmark Function
            for Optimization. Figure~\ref{fig.fun_bohachevsky} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_bohachevsky5} and~\ref{tab.fun_bohachevsky10} 
            (for five and ten dimensions, respectively). Due to the observation 
            and analysis of these results, we identify our proposed strategy 
            obtained solutions in the same order as the traditional Xover Mutation, 
            in a significantly reduced number of evaluations.

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_bohachevsky.pdf}
                \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Bohachevsky Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_bohachevsky5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Bohachevsky Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 7.28E-08 & 2.20E-08 & 15,010 & 24.2 \\
                \textbf{Elite Projection} & 4.51E-08 & 2.94E-08 & 8,266 & 12.6 \\
                \textbf{All Random} & 6.16E-08 & 2.85E-08 & 11,998 & 21.7 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Bohachevsky Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_bohachevsky10}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Bohachevsky Function - 10 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 8.66E-08 & 1.38E-08 & 40,166 & 44.4 \\
                \textbf{Elite Projection} & 3.80E-08 & 3.34E-08 & 8,506 & 12.9 \\
                \textbf{All Random} & 5.34E-08 & 3.76E-08 & 19,537 & 26.8 \\ \bottomrule
                \end{tabular}
                \end{table}

            \FloatBarrier

        \subsubsection{Griewank Benchmark Function Experiment}

            The third experiment objective was to confirm Animal Life Cycle
            Algorithm continued finding solutions in a reduced number of
            evaluations. For this test, we selected the Griewank Benchmark
            Function for Optimization. Figure~\ref{fig.fun_griewank} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_griewank5} and~\ref{tab.fun_griewank10} 
            (for five and ten dimensions, respectively). With this analysis, 
            we confirmed our strategy continued to obtain solutions in the same 
            order as expected, in a reduced number of evaluations and less time.

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_griewank.pdf}
                \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Griewank Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_griewank5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Griewank Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 6.92E-08 & 2.40E-08 & 44,566 & 48.3 \\
                \textbf{Elite Projection} & 3.77E-08 & 2.74E-08 & 16,412 & 20.1 \\
                \textbf{All Random} & 5.63E-08 & 2.99E-08 & 35,761 & 38.5 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Griewank Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_griewank10}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Griewank Function - 10 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 8.07E-08 & 1.39E-08 & 92,885 & 100.0 \\
                \textbf{Elite Projection} & 4.21E-08 & 3.40E-08 & 13,534 & 17.3 \\
                \textbf{All Random} & 5.08E-08 & 3.54E-08 & 40,544 & 52.5 \\ \bottomrule
                \end{tabular}
                \end{table}

            \FloatBarrier

        \subsubsection{Rastrigin Benchmark Function Experiment}

            This experiment's goal was to follow and study the behavior of our
            proposed strategy, to repeat the results in the same order as
            expected, in a reduced number of both time and evaluations. We
            selected Rastrigin Classic Benchmark Function for Optimization for
            this experiment. Figure~\ref{fig.fun_rastrigin} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_rastrigin5} and~\ref{tab.fun_rastrigin10} 
            (for five and ten dimensions, respectively).

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rastrigin.pdf}
                \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Rastrigin Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rastrigin5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Rastrigin Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 7.85E-08 & 1.59E-08 & 22,322 & 34.1 \\
                \textbf{Elite Projection} & 4.42E-08 & 3.26E-08 & 10,860 & 14.8 \\
                \textbf{All Random} & 5.66E-08 & 2.81E-08 & 21,122 & 35.0 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Rastrigin Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rastrigin10}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Rastrigin Function - 10   Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 8.56E-08 & 1.23E-08 & 53,579 & 58.7 \\
                \textbf{Elite Projection} & 3.17E-08 & 2.57E-08 & 8,704 & 13.0 \\
                \textbf{All Random} & 5.00E-08 & 3.16E-08 & 24,376 & 27.4 \\ \bottomrule
                \end{tabular}
                \end{table}

            \FloatBarrier

        \subsubsection{Sphere Benchmark Function Experiment}

            For our fifth experiment we chose the Sphere Classic Benchmark
            Function for Optimization. Even though the sphere function is
            considered one of the simplest to solve, the same behavior was
            consistent for the algorithm, where it showed a reduced number of
            evaluations and execution time. We can confirm this affirmation
            with the results shown in this experiment.
            Figure~\ref{fig.fun_sphere} displays its corresponding Box and
            Whisker chart, where we summarized the results in
            Tables~\ref{tab.fun_sphere5} and~\ref{tab.fun_sphere10} (for
            five and ten dimensions, respectively).

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_sphere.pdf}
                \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Sphere Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_sphere5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Sphere Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 7.82E-08 & 1.65E-08 & 11,312 & 14.5 \\
                \textbf{Elite Projection} & 3.60E-08 & 3.27E-08 & 7,056 & 10.9 \\
                \textbf{All Random} & 6.14E-08 & 2.79E-08 & 9,158 & 12.2 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Sphere Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_sphere10}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Sphere Function - 10 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 8.39E-08 & 1.45E-08 & 30,769 & 34.4 \\
                \textbf{Elite Projection} & 4.28E-08 & 3.06E-08 & 9,236 & 13.3 \\
                \textbf{All Random} & 5.32E-08 & 3.38E-08 & 21,465 & 26.3 \\ \bottomrule
                \end{tabular}
                \end{table}

            \FloatBarrier

        \subsubsection{Rosenbrock Benchmark Function Experiment}

            The goal of our sixth and last experiment was to study the behavior
            of the Animal Life-Cycle Algorithm when tested with the Rosenbrock
            Benchmark Function for Optimization. From all of our previous
            evaluation functions, Rosenbrock presented the most difficult
            challenge for our algorithm. This test facilitated the
            differentiation between the three compared strategies because the
            solutions found were in different numeric order. After all tests,
            the Elite Projection proved to be the best alternative. We can
            corroborate this by analyzing Figures~\ref{fig.fun_rosenbrock_5d}
            and~\ref{fig.fun_rosenbrock_10d}, which shows its corresponding Box
            and Whisker chart. We present the summarized results in
            Tables~\ref{tab.fun_rosenbrock5} and~\ref{tab.fun_rosenbrock10}
            (for five and ten dimensions, respectively).

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rosenbrock_5d.pdf}
                \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 5 Dimensions.} \label{fig.fun_rosenbrock_5d}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Rosenbrock Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rosenbrock5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Rosenbrock Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 4.65E-03 & 8.29E-03 & 500,000 & 646.4 \\
                \textbf{Elite Projection} & 9.62E-07 & 1.86E-06 & 307,878 & 427.0 \\
                \textbf{All Random} & 8.30E-06 & 1.58E-05 & 491,400 & 697.8 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rosenbrock_10d.pdf}
                \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 10 Dimensions.} \label{fig.fun_rosenbrock_10d}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Rosenbrock Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rosenbrock10}        
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Rosenbrock Function - 10 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 1.35E+00 & 9.83E-01 & 1,000,000 & 1,384.3 \\
                \textbf{Elite Projection} & 4.26E-02 & 4.34E-02 & 1,000,000 & 1,146.0 \\
                \textbf{All Random} & 4.27E-02 & 6.02E-02 & 952,038 & 1,147.8 \\ \bottomrule
                \end{tabular}
                \end{table}

            \FloatBarrier

\section{Discussion}
    \label{section.discussion}

    Imagine being an astronaut on a mission repairing a space station in the
    middle of space. Suddenly, a block of asteroids hits the craft, and you
    lose your oxygen tank while the explosion pushes you away. From afar, you
    see the area where your tank might be, covered with something similar to a
    gas leaked from the station that blocks all visibility. Finding the tank is
    the only hope to return to your main ship some miles away. The oxygen
    reserve from your suit is running out, and there are only a couple of
    minutes left. Now hold your breath in real life and think, what strategy
    will you choose to search for your tank? We repeated this mental exercise
    several times until we found the best solution (or blacked out).

    If your life depended on it, would you choose a Genetic Algorithm, a
    variant of a Particle Swarm Optimization Algorithm, or another? We searched
    for a way to mix both, at least in some way, take the main idea or concepts
    from them and make them work together. We strongly believe it is possible
    to combine the features, as previous work has proven to obtain outstanding
    results \cite{garcia2015evospace,garcia2021event,valdez2021container,valdez2021swarm}.
    Our goal was to create a swarm out of the best individuals found in
    evolution. We probably have a long way to go, but at least we are getting
    promising results. From our experiments, all six Classic Benchmark
    Functions for Optimization (Ackley, Bohachevsky, Griewank, Rastrigin,
    Sphere, and Rosenbrock) proved the same behavior for the Animal Life Cycle
    Algorithm: finding the expected solution in a reduced number of evaluations
    and less execution time.

\section{Conclusions}
    \label{section.conclusions}

    The Animal Life Cycle Algorithm allows for multiple parameters'
    fine-tuning, facilitating the freedom to experiment with different
    alternatives to restart the population and solve extinction caused by
    nature's pressure, which will impact how quickly, and the quality of its
    found solution. We compared the results obtained with the use of historical
    elite projection versus other alternatives, using classic benchmark
    functions for optimization for comparison, where it showed favorable and
    promising results.

    As the nature of the challenge increases, it is indispensable to have an
    elastic, scalable, and fault-tolerant model designed with cloud
    collaboration processes, and asynchronous communication. We have proven
    that it is possible to evolve a population, using a distributed, parallel,
    and asynchronous strategy, inspired by the Genetic Algorithm (GA). To
    further validate this work, we could use some more demanding (or control)
    problem that requires calculating real numbers
    \cite{stanley2002evolving,miikkulainen2019evolving}. We implemented the
    algorithm using Docker containers.

\begin{acknowledgement}
    This paper has been supported in part by TecNM Project 15340.22-P.
\end{acknowledgement}

% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%

\bibliographystyle{splncs03_unsrt}
%\bibliographystyle{splncs04}
\bibliography{bib/bibliografia.bib}

\end{document}

% TO-DO: Turnitin.

### 2023-09-14 paper.tex
First change from overleaf.
Halfway update (start of experimental results).

@@
 \usepackage[section]{placeins} % Forces an image to be displayed in it's section
-
 %\usepackage{draftwatermark}
@@
 This paper focuses on breeding, whereas in earlier versions of the algorithm, we used the traditional GA one-point crossover.
-In this paper, we propose a different alternative to the classical approach, where part of the genetic information is directly copied to each of the offsprings in the crossover operator, where this type of crossover may not perform well in continuous optimization problems.
+In this paper, we propose a different alternative to the classical approach, where part of the genetic information is directly copied to each of the offspring in the crossover operator, where this type of crossover may not perform well in continuous optimization problems.
 In this proposal, we use the parent's genetic information for each gene, using those values as lower and upper bounds of a range, where a random value within that range determines the new value for that gene index of the offspring.
@@
 We expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals.
-In this paper, we use the benchmark functions introduced in the competition on evolutionary computation for the 2017 edition (CEC2017) to compare the traditional one-point crossover and our proposed strategy.
+In this paper, we use the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC2017) to compare the traditional one-point crossover and our proposed strategy.
 Experimental results indicate that our proposed operator may be a good alternative for the canonical crossover.}
@@
 
-    Biologically inspired algorithms have proven to be very effective when
-    solving complex optimization problems
-    \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but
-    the more challenging the problem, the more computing power it will require
-    to solve them \cite{ontiveros2018high}. We consider the main reason it requires 
-    more computing power is related to the evaluation of the fitness function, 
-    which means calculating the solution to the real problem our algorithm is searching for. 
-    One technique to manage this
-    processing power demand is to use distributed computing
-    \cite{thain2005distributed} or the cloud resources 
-    \cite{garcia2013there,eshratifar2019bottlenet}. This strategy allows adaptation 
-    of the required computing need according to the problem's complexity.
+    Biologically inspired algorithms are a very effective technique to solve complex optimization problems\cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}.
+Traditionally, nature-inspired algorithms are developed with a sequential perspective\cite{porto2018evolutionary,back1996evolutionary},  meaning that all tasks execute one step at a time, where all processes must wait for the previous to finish before continuing (synchronous perspective).
+Some architectures address this issue by working on the cloud\cite{valdez2021container,garcia2015evospace,merelo2016nodio} and finding solutions on distributed technologies.
 
-    Traditionally, bio-inspired algorithms are developed with a sequential
-    (synchronous) perspective
-    \cite{porto2018evolutionary,back1996evolutionary}, where a process must
-    pause for the previous task to finish before continuing. 
-    Some architectures address this issue \cite{valdez2021container,garcia2015evospace,merelo2016nodio} 
-    by working on the cloud and finding solutions on distributed technologies.
-    In this research, we present a distributed algorithm totally built as a 
-    native cloud solution, where its processes execute asynchronously and in 
-    parallel, managing the processing workload among several computers.  
-    This strategy allows to elastically increase (or reduce) the
-    computing power according to the nature of the challenge
-    \cite{armbrust2010view}.
+    In previous work, we introduced a population-based, bio-inspired algorithm\cite{Felix-Saul2022,Felix-Saul2023}.
+The proposed algorithm is inspired by the biological animal life cycle, consisting of the stages\cite{read1968system} of birth, growth, reproduction, and death.
+Our algorithm was initially based on the canonical Genetic Algorithm (GA)\cite{holland1992genetic,holland1984genetic}, where all the individuals have a genotype (chromosome).
+Our algorithm’s goal is to mimic the animal life cycle, where at any given moment, new individuals are born to be part of the population and participate in the collective evolution.
+As time passes, they grow older and mature, suffering changes throughout their lives that we chose to represent as mutations.
 
-    In previous work, we introduced an algorithm inspired by the biological
-    life-cycle of animal species \cite{Felix-Saul2022}. As in nature, population individuals grow older
-    and age. In this algorithm's reproduction process, couples must match by mutual
-    attraction, where sometimes individuals won't procreate offspring because of
-    the mate's low appeal. As time passes, the environment kills its individuals
-    either because of low fitness or age, causing occasional population extinction.
+    In our analysis, we thought of death’s work to maintain balance in the population by enforcing the survival of the fittest.
+As in life, death can happen to everyone: from a newborn to the elderly, where fitness will determine the individual’s longevity.
+This algorithm was inspired by the traditional Genetic Algorithm \cite{holland1992genetic,holland1984genetic}, meaning that all individuals have a genotype (chromosome) that is a list of values.
+We calculate the individual’s fitness with the evaluation function and do crossover and mutation to the population.
 
-    We define extinction as a situation in which something no longer exists; in
-    our case scenario, when we refer to extinction in our algorithm, it means
-    the population of individuals no longer exists. When this condition
-    presents itself, it is required to create a new population to continue
-    evolution (restart).
+    What makes our strategy different is that we don’t use the concept of evolutionary generations.
+We manage our set of solutions as a whole that continuously evolve over time.
+Allowing individuals of different ages to breed and generate offspring, as it happens in nature.
+One difference to highlight in our algorithm is that both the crossover (reproduction) and mutation (growth) are executed through independent processes that randomly affect the population.
+We display the general model concept for the Animal Life Cycle Algorithm (ALCA) in Figure~\ref{fig.algorithm_model}.
 
-    Population restart is the process in which we create a
-    new set of individuals to replace the others that have already died (or
-    were discarded) due to their aptitude. In a previous work \cite{Felix-Saul2022} 
-    we used to generate a new random set of solutions, with the cost of losing 
-    all evolution knowledge. In the state of the art, we have found other methodologies 
-    that have successfully sought to solve the problem of population extinction with
-    restarts \cite{hellwig2020modified, loshchilov2013cma, jansen2010aging, tendresse2001effects, mathias1998effects}.
+    In this research, we propose a new alternative for reproduction, a new breeding crossover approach for evolutionary algorithms using the classic one-point crossover as a reference to our proposal.
+We performed comparison experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) for evaluation.
+We finalize with a statistical Z-Test with a 95 percent confidence level to determine the best alternative.
 
-    One contribution of this paper is to prove that it is possible to
-    evolve a population of individuals, similar to a Genetic Algorithm (GA),
-    using a distributed, parallel, and asynchronous methodology by algorithm
-    implementation and testing.
+    We organized this paper in the following structure.
+First, we illustrate our alternative crossover proposal, from the inspiration to a detailed example.
+We compare the canonical one-point crossover with our proposed solution in section~\ref{section.proposal}, followed by our experiment configuration and results in section~\ref{section.experiments}, where we analyze and describe some of our research findings in section~\ref{section.discussion}.
+We finalize by presenting some inferences based on the results of our experiments in section~\ref{section.conclusions}.
 
-    The main contribution of this research is to demonstrate how to improve the
-    algorithm's behavior, by solving population extinction caused by nature's
-    pressure in the Animal Life Cycle Algorithm with one of the most promising
-    alternatives: the projection of the Elite towards the Champion. To validate
-    our findings, we compare the results obtained with the latter and the
-    random use of the more traditional alternatives (mutation and crossover),
-    using classic benchmark functions for optimization for comparison.
-
-    This paper is organized as follows. First, we 
-    illustrate our algorithm model, the encountered problem with the occasional
-    population extinction, and our proposed solution in
-    section~\ref{section.proposal}, followed by our experimental configuration and
-    results in section~\ref{section.experiments}, where we continue to analyze and
-    describe some of our research findings in section~\ref{section.discussion}. We
-    finalize by presenting some inferences based on the results of our experiments
-    in section~\ref{section.conclusions}.
+    \begin{figure}[!ht]
+        \centering
+        \includegraphics[width=0.90\linewidth]{img/fig_algorithm_model.pdf}
+        \caption{Animal Life Cycle Algorithm model.} \label{fig.algorithm_model}
+        \end{figure}
 
@@
 
-    In previous work, we presented an algorithm inspired by nature 
-    \cite{Felix-Saul2022}, where we model our algorithm based on
-    the generalization of the life cycle of animal species. Our algorithm, as
-    in nature, consists of four stages \cite{read1968system}: birth, growth,
-    reproduction, and death. One key concept of our idea is that combining
-    those processes evolves the population. We propose to execute all these
-    stages in parallel and asynchronously on a continuously evolving
-    population.
+    Let's imagine that colors black and white fell in love and had beautiful children.
+If we had to guess what color their offspring would be, it could only be predictable its children's color would be inside the domain shown in Figure~\ref{fig.grayscale_continuous}.
 
-    \subsection{Algorithm Model}
-
-        This algorithm was inspired by the traditional Genetic Algorithm,
-        meaning that all individuals have a genotype (chromosome) that is a
-        list of values. We calculate the individual's fitness with the
-        evaluation function and do crossover and mutation to the population.
-        What makes our strategy different is that we don't use the concept of
-        evolutionary generations. We manage our set of solutions as a whole
-        that continuously evolve over time. Allowing individuals of different
-        ages to breed and generate offspring, as it happens in nature. The
-        crossover and mutation execute as independent processes that randomly
-        affect the individuals.
-
-        Our algorithm's goal is to mimic the animal life cycle, where at any
-        given moment, new individuals are born to be part of the population and
-        participate in the collective evolution. As time passes, they grow
-        older and mature, suffering changes throughout their lives that we
-        chose to represent as mutations. In our analysis, we considered a
-        couple's attraction a fundamental factor in reproduction. We thought of
-        death's work to maintain balance in the population by enforcing the
-        survival of the fittest. As in life, death can happen to everyone: from
-        a newborn to the elderly, where fitness will determine the individual's
-        longevity. We display the general model concept in
-        Figure~\ref{fig.algorithm_model}.
-
-        \subsubsection{Birth} Birth is the first step of the population's
-        evolution. For the algorithm representation, we begin with the
-        generation of a randomly set of individuals.
-
-        \subsubsection{Growth} In our algorithm representation, there is a
-        direct correlation between elapsed time and the population's evolution.
-        For this to be possible in our proposal, all individuals must grow
-        older and change as time progresses. With each increment of age, an
-        individual may improve or deteriorate. We chose to manifest this idea
-        by performing a small mutation in each change.
-
-        \subsubsection{Reproduction} In this step, we select a random pair of
-        individuals and evaluate their couple's attraction, where fitness will
-        be the decisive factor that impacts its value. The higher the fitness
-        of the individual, the more attractive it will appear to fellow
-        individuals. As a consequence of the previous concept, we can
-        anticipate that not all couples will produce offspring, meaning
-        reproduction will not always be successful.
-
-        \subsubsection{Death} Death is the last step of the animal life cycle,
-        as in our algorithm. We chose death as a representation of all the
-        environmental challenges for survival, where its execution enforces the
-        survival of the fittest. As time progresses, so does increase nature's
-        level of danger. The better the individual fitness will increase its
-        chances of survival.
-
-        \begin{figure}
+    \begin{figure}[!ht]
         \centering
-            \includegraphics[width=100mm]{img/fig_algorithm_model.pdf}
-            \caption{Animal Life Cycle Algorithm model.} \label{fig.algorithm_model}
+        \includegraphics[width=0.70\linewidth]{img/fig_grayscale_continuous.pdf}
+        \caption{Black and white offspring predictable color domain.} \label{fig.grayscale_continuous}
         \end{figure}
 
-    \subsection{Problem}
+    If we replace colors black and white with values 0 and 1 respectively, how many values can we find in between?
+We could replace attributes, switching from color to height, strength, agility, or any other feature we might need to focus on.
+The parents' attribute values will determine how their offspring's attributes are defined.
+This paper focuses on breeding (or reproduction), whereas in earlier versions of the algorithm, we used the traditional (GA) one-point crossover.
 
-        In this algorithm's reproduction process, we find mating couples by mutual
-        attraction, where sometimes individuals won't procreate offspring because of
-        the mate's low appeal. As time passes, the environment could kill its
-        individuals either because they have low fitness or age, leading to extinction,
-        meaning there are no more individuals in the population left to reproduce. When
-        this condition presents, if evaluations are available and termination
-        conditions enable the algorithm to continue the search, it is required to
-        create a new set of individuals. We illustrate the general flowchart for the
-        Life-Cycle algorithm in Figure~\ref{fig.flowchart}.
+    \subsection{Crossover Proposal}
 
-        \begin{figure}
-            \includegraphics[width=\textwidth]{img/fig_flowchart.pdf}
-            \caption{Animal Life-Cycle Algorithm general flowchart.} \label{fig.flowchart}
+    In this paper, we propose a different alternative to the classical approach, where part of the genetic information is directly copied to each of the offspring in the crossover operator, where this type of crossover may not perform well in continuous optimization problems.
+We provide an example of the One Point Crossover in Figure~\ref{fig.onepoint_crossover}.
+
+    \begin{figure}[!ht]
+        \centering
+        \includegraphics[width=0.70\linewidth]{img/fig_onepoint_crossover.pdf}
+        \caption{Classical approach example for the One Point Crossover, with crossover point 3.} \label{fig.onepoint_crossover}
         \end{figure}
 
-    \subsection{Proposed Solution}
-        % It is important to do a literature review for the following papers, there are 
-        % other works that tackle similar problems or use it as a strategy. - M 
-        In this article, we test various strategies to generate a new population to
-        replace individuals that have already died (or were discarded) due to their
-        aptitude, as happens in the life cycle. We previously used to generate a new
-        random set of solutions, with the cost of losing all evolution knowledge.
+    In this proposal, we use the parent's genetic information for each gene, using those values as lower and upper bounds of a range, where a random value within that range determines the new value for that gene index of the offspring.
+Our proposal example for the Continuous Range Crossover is displayed in Figure~\ref{fig.contrange_crossover}, where it should be noted that we construct a template that will be used for all the offspring generated by each couple.
 
-        This article proposes some strategies to carry out this operation,
-        where the presented distribution strategy obtained the best results. We
-        propose one promising alternative to restart the population, to solve
-        extinction caused by nature's pressure in the Life Cycle algorithm: the
-        projection of the historically best-found candidate solutions (Elite)
-        towards the best-found candidate solution (Champion).
-
-        The strategy we describe in this paper use an elite set, that includes
-        the historically best-found candidate solutions to take
-        advantage of the historical evolution. Our goal is for the offspring to
-        be somewhat close to the best individuals of the Elite.
-        We use the golden ratio to compute the distance between new individuals in the population, making
-        an improved distribution. We can consider our strategy an improvement 
-        over other alternatives because of the findings of our latter experiments.
-
-        Based on the historically best candidate
-        solution and the elite set, we use the Golden Ratio (shown in
-        Equation~\ref{eq.golden_ratio}) to compute the distance between new individuals
-        in the population, making an improved distribution. It randomly selects a
-        solution from the elite set and uses the Golden Ratio 
-        \cite{nematollahi2020novel, gaikwad2021face, khesin2022golden, sym13081334, https://doi.org/10.1111/nyas.14895} 
-        to compute multiple solutions against the best-found candidate.
-
-        \begin{equation}
-            \begin{matrix}\includegraphics[width=25mm]{img/eq_golden_ratio.pdf}\end{matrix}
-            \label{eq.golden_ratio}
-            \end{equation}
-
-        This strategy is how we can calculate the projection of the
-        historically Elite towards the Champion solution. To illustrate this
-        concept, we include Figure~\ref{fig.elite_projection}, placing the
-        Elite solution on the far right and the Champion solution on the left
-        corner. We can observe the higher amount of new solutions progressively
-        closer to the Champion.
-
-        \begin{figure}
+    \begin{figure}[!ht]
         \centering
-            \includegraphics[width=0.65\textwidth]{img/fig_elite_projection.pdf}
-            \caption{Projection of an Elite solution (found on the right) towards the Champion (at the left).} \label{fig.elite_projection}
-            \end{figure}
-
-        This process generates new solutions that will be the new population set. It
-        uses the Golden Ratio to progressively approximate from an Elite solution to
-        the Champion. This strategy facilitates to find apparently hidden solutions,
-        having an exploitation emphasis. Figure~\ref{fig.elite_projection_swarm}
-        displays the projection of five Elite solutions (on the corners) towards the
-        Champion (in the center).
-
-        \begin{figure}
-            \centering
-            \includegraphics[width=0.85\textwidth]{img/fig_elite_projection_swarm.pdf}
-            \caption{Projection of five Elite solutions towards the Champion, results in a mini-swarm.} \label{fig.elite_projection_swarm}
+        \includegraphics[width=0.70\linewidth]{img/fig_contrange_crossover.pdf}
+        \caption{Our proposal example for the Continuous Range Crossover mating the same couple of individuals.} \label{fig.contrange_crossover}
         \end{figure}
@@
 
-    As a proof-of-concept, we implemented the algorithm with Docker containers,
-    where we compare the results obtained with the projection of the Elite towards
-    the Champion strategy and the random use of the more traditional alternatives
-    (such as mutation and crossover), using classic benchmark functions for
-    optimization as implemented by the DEAP (Distributed Evolutionary Algorithms in
-    Python) library \cite{fortin2012deap}.
-
-    \subsection{Experimental Setup}
-
-        The following tables show the configuration used to execute the experiments for
-        the analysis and comparison in this paper. In
-        Table~\ref{tab.general_configuration}, we can find the General Configuration
-        for the Animal Life Cycle Algorithm. All values from this configuration
-        remained constant during all phases of the experiment runs. The following
-        table, Table~\ref{tab.benchmark_fun_config}, shows the values used for the
-        Classic Benchmark Functions for Optimization, where these are adjusted
-        accordingly for each function.
+    To validate our proposal, we performed experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) for evaluation to compare the traditional one-point crossover and our proposed strategy.
+We finalize with a statistical Z-Test with a ninety-five percent confidence level to determine the best alternative.
+Table~\ref{tab.benchmark_functions} lists the thirty mathematical benchmark functions used for evaluation, to obtain the comparison results shown in our research.
 
@@
     % \usepackage{booktabs}
-        % To change the size of the font use \scriptsize or \tiny
+    % \usepackage[table,xcdraw]{xcolor}
+    % If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
+    \begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Mathematical benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017).}\label{tab.benchmark_functions}    
+    \begin{tabular}{@{}cllcl@{}}
+    \toprule
+    \multicolumn{5}{c}{\textbf{CEC-2017 Mathematical Benchmark Functions}} \\ \midrule
+    \textbf{Fx} & \textbf{Function Name} &  & \textbf{Fx} & \textbf{Function Name} \\
+    F1 & Shifted and Rotated   Bent Cigar Function &  & F16 & Hybrid function 6 \\
+    F2 & Shifted and Rotated   Sum of Different Power Function &  & F17 & Hybrid function 7 \\
+    F3 & Shifted and Rotated   Zakharov Function &  & F18 & Hybrid function 8 \\
+    F4 & Shifted and Rotated   Rosenbrock's Function &  & F19 & Hybrid function 9 \\
+    F5 & Shifted and Rotated   Rastrigin's Function &  & F20 & Hybrid function 10 \\
+    F6 & Shifted and Rotated   Schaffer F7 Function &  & F21 & Composition function   1 \\
+    F7 & Shifted and Rotated   Lunacek Bi-Rastrigin's Function &  & F22 & Composition function   2 \\
+    F8 & Shifted and Rotated   Non-Continuous Rastrigin's Function &  & F23 & Composition function   3 \\
+    F9 & Shifted and Rotated   Levy Function &  & F24 & Composition function   4 \\
+    F10 & Shifted and Rotated   Schwefel's Function &  & F25 & Composition function   5 \\
+    F11 & Hybrid function 1 &  & F26 & Composition function   6 \\
+    F12 & Hybrid function 2 &  & F27 & Composition function   7 \\
+    F13 & Hybrid function 3 &  & F28 & Composition function   8 \\
+    F14 & Hybrid function 4 &  & F29 & Composition function   9 \\
+    F15 & Hybrid function 5 &  & F30 & Composition function   10 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+    \subsection{Experimental Configuration}
+
+    We used the Animal Life Cycle Algorithm (ALCA) for our experiments, switching between the breeding strategies (One Point and Continuous Range Crossover) with the same general setup.
+In Table~\ref{tab.general_configuration}, we can find the General Configuration used to run the experiments for our research, where all values from this configuration remained constant during all phases of the experiment runs.
+
+    For each of the thirty mathematical benchmark functions from the CEC-2017, we evaluated the ten and thirty dimensions, where we performed fifty-one runs per dimension.
+To find and determine the best alternative finalized with a statistical Z-Test with a ninety-five percent confidence level.
+
+    % Please add the following required packages to your document preamble:
+    % \usepackage{booktabs}
+    % \usepackage[table,xcdraw]{xcolor}
+    % If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
     \begin{table}[]
@@
     \multicolumn{2}{l}{\textbf{ALCA   General Configuration}} \\ \midrule
-            Function name & ALL \\
+    \textbf{Function name} & \textbf{ALL} \\
     Population & 500 \\
-            Target error & 1.00E-08 \\
+    Evaluations & 10,000 * Dim \\
     Crossover rate & 100 \\
     Mutation rate & 7 \\
-            Max age & 40 \\
+    Max age & 5 \\
     Tournament rep. & 100 \\
@@
 
-        \begin{table}[]
-            \scriptsize
-            \centering
-            \caption{Classic Benchmark Functions for Optimization Configuration.}\label{tab.benchmark_fun_config}
-            \begin{tabular}{@{}llllllll@{}}
-            \toprule
-            \multicolumn{8}{l}{\textbf{Benchmark Configuration Setup}} \\ \midrule
-            Function name & Ackley & Bohachevsky & Griewank & Rastrigin & Sphere & Rosenbrock & Rosenbrock \\
-            Dimensions & 5, 10 & 5, 10 & 5, 10 & 5, 10 & 5, 10 & 5 & 10 \\
-            Max evaluations & 200,000 & 200,000 & 200,000 & 200,000 & 200,000 & 500,000 & 1,000,000 \\
-            Max stagnation & 50,000 & 50,000 & 50,000 & 50,000 & 50,000 & 125,000 & 250,000 \\
-            Target fitness & -20.0 & -12.0 & -150.0 & -80.0 & -50.0 & -3500.0 & -3500.0 \\
-            Bound matrix & {[}-32, 32{]} & {[}-2, 2{]} & {[}-500, 500{]} & {[}-5, 5{]} & {[}-5, 5{]} & {[}-2, 2{]} & {[}-2, 2{]} \\ \bottomrule
-            \end{tabular}
-            \end{table}
-
     \FloatBarrier
 
-    \subsection{Experiment Results}
+    \subsection{Experimental Results}
+
+    We describe how to interpret the results presented in our Box and Whisker charts for each mathematical function.
+We display the ten and thirty-dimension charts on the left and right sides.
+We can find the results accumulated in 51 runs, in green color the One Point crossover, and in blue color the Continuous Range crossover.
+The closer the error results get to the zero value, the better.
+
+    STOP HERE --- A new beginning (this is an upload test).
 

### 2023-09-14 paper.tex
Work in progress (Discussion).

@@
 
-    STOP HERE --- A new beginning (this is an upload test).
+    \begin{figure}[!ht]
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F1x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F1x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F2x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F2x30D.pdf} 
+        \end{minipage}
 
-        For each experiment, we ran 30 independent executions per algorithm and
-        dimensions specified. We recorded the following results: best-found error average,
-        standard deviation, total number of evaluations, and total elapsed time (in
-        seconds). The labels used on the results of our summarized experiments tables
-        are the following:
-
-        \begin{itemize}
-            \item   Error:       is the best-found error average.
-            \item   St-Dev:      is the standard deviation calculated from the error. 
-            \item   Evals.:      is the total number of evaluations the algorithm executed.
-            \item   Time:        is the total elapsed or wall clock time, in seconds. 
-        \end{itemize}
-
-        The alternatives to restart this new population are the creation of a new set
-        of candidate solutions based on either: 1. Crossing the Champion with the Elite;
-        2. The mutation with uniform modification from the Elite; 3. The
-        projection of the Elite towards the Champion; 4. Based on random use of the
-        previous alternatives. We compared three strategies by grouping the previous
-        alternatives in the following:
-
-        \begin{itemize}
-            \item   Xover Mutation:      Crossing the Champion with the Elite, and the mutation with uniform modification from the Elite.
-            \item   Elite Projection:    The projection of the Elite towards the Champion. 
-            \item   All Random:          Based on random use of the previous alternatives.
-        \end{itemize}
-
-        \subsubsection{Ackley Benchmark Function Experiment}
-
-            The goal of the first experiment was to confirm that this paper’s
-            proposed strategy obtained improved results over our basic
-            technique, which created a new population with a random generation
-            of a new set of candidate solutions. We chose Ackley as the first
-            Classic Benchmark Function for Optimization to test our algorithm
-            behavior, where Figure~\ref{fig.fun_ackley} shows its corresponding
-            Box and Whisker chart, and we summarized the results in
-            Tables~\ref{tab.fun_ackley5} and~\ref{tab.fun_ackley10} (for five 
-            and ten dimensions, respectively).
-
-            \begin{figure}
-                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_ackley.pdf}
-                \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
+        \caption{Box and Whisker charts for mathematical functions F1 and F2.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F1-F2}
     \end{figure}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Ackley Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_ackley5}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Ackley Function - 5 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 8.69E-08 & 1.36E-08 & 46,331 & 49.9 \\
-                \textbf{Elite Projection} & 6.33E-08 & 2.70E-08 & 13,811 & 18.1 \\
-                \textbf{All Random} & 6.78E-08 & 2.55E-08 & 30,236 & 32.8 \\ \bottomrule
-                \end{tabular}
-                \end{table}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Ackley Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_ackley10}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Ackley Function - 10 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 9.35E-08 & 5.93E-09 & 104,842 & 111.7 \\
-                \textbf{Elite Projection} & 5.11E-08 & 3.13E-08 & 16,019 & 20.1 \\
-                \textbf{All Random} & 6.89E-08 & 2.75E-08 & 43,631 & 46.3 \\ \bottomrule
-                \end{tabular}
-                \end{table}
 
@@
 
-        \subsubsection{Bohachevsky Benchmark Function Experiment}
+    \begin{figure}[!ht]
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F3x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F3x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F4x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F4x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F5x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F5x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F6x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F6x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F7x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F7x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F8x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F8x30D.pdf} 
+        \end{minipage}
 
-            As our second experiment to further validate and prove our
-            algorithm behavior, we chose Bohachevsky Classic Benchmark Function
-            for Optimization. Figure~\ref{fig.fun_bohachevsky} shows its
-            corresponding Box and Whisker chart, where we summarized the
-            results in Tables~\ref{tab.fun_bohachevsky5} and~\ref{tab.fun_bohachevsky10} 
-            (for five and ten dimensions, respectively). Due to the observation 
-            and analysis of these results, we identify our proposed strategy 
-            obtained solutions in the same order as the traditional Xover Mutation, 
-            in a significantly reduced number of evaluations.
-
-            \begin{figure}
-                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_bohachevsky.pdf}
-                \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
+        \caption{Box and Whisker charts for mathematical functions F3 to F8.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F3-F8}
     \end{figure}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Bohachevsky Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_bohachevsky5}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Bohachevsky Function - 5 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 7.28E-08 & 2.20E-08 & 15,010 & 24.2 \\
-                \textbf{Elite Projection} & 4.51E-08 & 2.94E-08 & 8,266 & 12.6 \\
-                \textbf{All Random} & 6.16E-08 & 2.85E-08 & 11,998 & 21.7 \\ \bottomrule
-                \end{tabular}
-                \end{table}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Bohachevsky Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_bohachevsky10}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Bohachevsky Function - 10 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 8.66E-08 & 1.38E-08 & 40,166 & 44.4 \\
-                \textbf{Elite Projection} & 3.80E-08 & 3.34E-08 & 8,506 & 12.9 \\
-                \textbf{All Random} & 5.34E-08 & 3.76E-08 & 19,537 & 26.8 \\ \bottomrule
-                \end{tabular}
-                \end{table}
 
@@
 
-        \subsubsection{Griewank Benchmark Function Experiment}
+    \begin{figure}[!ht]
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F9x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F9x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F10x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F10x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F11x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F11x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F12x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F12x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F13x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F13x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F14x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F14x30D.pdf} 
+        \end{minipage}
 
-            The third experiment objective was to confirm Animal Life Cycle
-            Algorithm continued finding solutions in a reduced number of
-            evaluations. For this test, we selected the Griewank Benchmark
-            Function for Optimization. Figure~\ref{fig.fun_griewank} shows its
-            corresponding Box and Whisker chart, where we summarized the
-            results in Tables~\ref{tab.fun_griewank5} and~\ref{tab.fun_griewank10} 
-            (for five and ten dimensions, respectively). With this analysis, 
-            we confirmed our strategy continued to obtain solutions in the same 
-            order as expected, in a reduced number of evaluations and less time.
-
-            \begin{figure}
-                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_griewank.pdf}
-                \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
+        \caption{Box and Whisker charts for mathematical functions F9 to F14.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F9-F14}
     \end{figure}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Griewank Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_griewank5}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Griewank Function - 5 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 6.92E-08 & 2.40E-08 & 44,566 & 48.3 \\
-                \textbf{Elite Projection} & 3.77E-08 & 2.74E-08 & 16,412 & 20.1 \\
-                \textbf{All Random} & 5.63E-08 & 2.99E-08 & 35,761 & 38.5 \\ \bottomrule
-                \end{tabular}
-                \end{table}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Griewank Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_griewank10}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Griewank Function - 10 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 8.07E-08 & 1.39E-08 & 92,885 & 100.0 \\
-                \textbf{Elite Projection} & 4.21E-08 & 3.40E-08 & 13,534 & 17.3 \\
-                \textbf{All Random} & 5.08E-08 & 3.54E-08 & 40,544 & 52.5 \\ \bottomrule
-                \end{tabular}
-                \end{table}
 
@@
 
-        \subsubsection{Rastrigin Benchmark Function Experiment}
+    \begin{figure}[!ht]
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F15x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F15x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F16x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F16x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F17x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F17x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F18x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F18x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F19x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F19x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F20x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F20x30D.pdf} 
+        \end{minipage}
 
-            This experiment's goal was to follow and study the behavior of our
-            proposed strategy, to repeat the results in the same order as
-            expected, in a reduced number of both time and evaluations. We
-            selected Rastrigin Classic Benchmark Function for Optimization for
-            this experiment. Figure~\ref{fig.fun_rastrigin} shows its
-            corresponding Box and Whisker chart, where we summarized the
-            results in Tables~\ref{tab.fun_rastrigin5} and~\ref{tab.fun_rastrigin10} 
-            (for five and ten dimensions, respectively).
-
-            \begin{figure}
-                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rastrigin.pdf}
-                \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
+        \caption{Box and Whisker charts for mathematical functions F15 to F20.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F15-F20}
     \end{figure}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Rastrigin Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rastrigin5}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Rastrigin Function - 5 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 7.85E-08 & 1.59E-08 & 22,322 & 34.1 \\
-                \textbf{Elite Projection} & 4.42E-08 & 3.26E-08 & 10,860 & 14.8 \\
-                \textbf{All Random} & 5.66E-08 & 2.81E-08 & 21,122 & 35.0 \\ \bottomrule
-                \end{tabular}
-                \end{table}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Rastrigin Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rastrigin10}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Rastrigin Function - 10   Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 8.56E-08 & 1.23E-08 & 53,579 & 58.7 \\
-                \textbf{Elite Projection} & 3.17E-08 & 2.57E-08 & 8,704 & 13.0 \\
-                \textbf{All Random} & 5.00E-08 & 3.16E-08 & 24,376 & 27.4 \\ \bottomrule
-                \end{tabular}
-                \end{table}
 
@@
 
-        \subsubsection{Sphere Benchmark Function Experiment}
+    \begin{figure}[!ht]
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F21x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F21x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F22x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F22x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F23x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F23x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F24x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F24x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F25x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F25x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F26x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F26x30D.pdf} 
+        \end{minipage}
 
-            For our fifth experiment we chose the Sphere Classic Benchmark
-            Function for Optimization. Even though the sphere function is
-            considered one of the simplest to solve, the same behavior was
-            consistent for the algorithm, where it showed a reduced number of
-            evaluations and execution time. We can confirm this affirmation
-            with the results shown in this experiment.
-            Figure~\ref{fig.fun_sphere} displays its corresponding Box and
-            Whisker chart, where we summarized the results in
-            Tables~\ref{tab.fun_sphere5} and~\ref{tab.fun_sphere10} (for
-            five and ten dimensions, respectively).
-
-            \begin{figure}
-                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_sphere.pdf}
-                \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}
+        \caption{Box and Whisker charts for mathematical functions F21 to F26.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F21-F26}
     \end{figure}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Sphere Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_sphere5}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Sphere Function - 5 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 7.82E-08 & 1.65E-08 & 11,312 & 14.5 \\
-                \textbf{Elite Projection} & 3.60E-08 & 3.27E-08 & 7,056 & 10.9 \\
-                \textbf{All Random} & 6.14E-08 & 2.79E-08 & 9,158 & 12.2 \\ \bottomrule
-                \end{tabular}
-                \end{table}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Sphere Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_sphere10}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Sphere Function - 10 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 8.39E-08 & 1.45E-08 & 30,769 & 34.4 \\
-                \textbf{Elite Projection} & 4.28E-08 & 3.06E-08 & 9,236 & 13.3 \\
-                \textbf{All Random} & 5.32E-08 & 3.38E-08 & 21,465 & 26.3 \\ \bottomrule
-                \end{tabular}
-                \end{table}
 
@@
 
-        \subsubsection{Rosenbrock Benchmark Function Experiment}
+    \begin{figure}[!ht]
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F27x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F27x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F28x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F28x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F29x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F29x30D.pdf} 
+        \end{minipage}
+        \vfill
+        \vspace{0.05 cm}
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F30x10D.pdf} 
+        \end{minipage}
+        \hfill
+        \begin{minipage}[h]{0.49\linewidth}
+            \includegraphics[width=1\linewidth]{img/fig_experiment_F30x30D.pdf} 
+        \end{minipage}
 
-            The goal of our sixth and last experiment was to study the behavior
-            of the Animal Life-Cycle Algorithm when tested with the Rosenbrock
-            Benchmark Function for Optimization. From all of our previous
-            evaluation functions, Rosenbrock presented the most difficult
-            challenge for our algorithm. This test facilitated the
-            differentiation between the three compared strategies because the
-            solutions found were in different numeric order. After all tests,
-            the Elite Projection proved to be the best alternative. We can
-            corroborate this by analyzing Figures~\ref{fig.fun_rosenbrock_5d}
-            and~\ref{fig.fun_rosenbrock_10d}, which shows its corresponding Box
-            and Whisker chart. We present the summarized results in
-            Tables~\ref{tab.fun_rosenbrock5} and~\ref{tab.fun_rosenbrock10}
-            (for five and ten dimensions, respectively).
-
-            \begin{figure}
-                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rosenbrock_5d.pdf}
-                \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 5 Dimensions.} \label{fig.fun_rosenbrock_5d}
+        \caption{Box and Whisker charts for mathematical functions F27 to F30.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F27-F30}
     \end{figure}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Rosenbrock Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rosenbrock5}
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Rosenbrock Function - 5 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 4.65E-03 & 8.29E-03 & 500,000 & 646.4 \\
-                \textbf{Elite Projection} & 9.62E-07 & 1.86E-06 & 307,878 & 427.0 \\
-                \textbf{All Random} & 8.30E-06 & 1.58E-05 & 491,400 & 697.8 \\ \bottomrule
-                \end{tabular}
-                \end{table}
-
-            \begin{figure}
-                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rosenbrock_10d.pdf}
-                \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 10 Dimensions.} \label{fig.fun_rosenbrock_10d}
-                \end{figure}
-
-            \begin{table}[]
-                \scriptsize
-                \centering
-                \caption{Rosenbrock Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rosenbrock10}        
-                \begin{tabular}{@{}lllll@{}}
-                \toprule
-                \multicolumn{5}{l}{\textbf{Rosenbrock Function - 10 Dimensions}} \\ \midrule
-                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
-                \textbf{Xover Mutation} & 1.35E+00 & 9.83E-01 & 1,000,000 & 1,384.3 \\
-                \textbf{Elite Projection} & 4.26E-02 & 4.34E-02 & 1,000,000 & 1,146.0 \\
-                \textbf{All Random} & 4.27E-02 & 6.02E-02 & 952,038 & 1,147.8 \\ \bottomrule
-                \end{tabular}
-                \end{table}
 
@@
     \label{section.discussion}
+
+    For each experiment, we ran fifty-one independent executions per CEC-2017 mathematical benchmark function and dimensions specified.
+We recorded the following results: best-found error average, standard deviation, and calculated the statistical Z-Test value.
+The labels used on the results of our summarized results tables are the following:
+
+    \begin{itemize}
+        \item   Fx:          is the mathematical benchmark function.
+        \item   Mean:        is the best-found error average.
+        \item   St-Dev:      is the standard deviation calculated from the error. 
+        \item   Z:           is the calculated statistical Z-Test value.
+    \end{itemize}
+
+    To find and determine the best alternative finalized with a statistical Z-Test with a 95 percent confidence level.
+Here are the results statistics values: Table 3 shows the condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions (D) for alternatives One Point and Continuous Range crossover; Table 4 displays the condensed ALCA evaluation results for the CEC-2017 mathematical operations running on thirty D for the same crossover alternatives.
+
+    We performed the statistical Z-Test for both crossover alternatives with a 95 percent confidence level.
+When the One Point passes the test, it is highlighted in green color.
+When the Continuous Range passes the statistical test, it is highlighted in blue.
+Where we did not find enough evidence to declare one choice as the best alternative, no Z value was highlighted.
+
+    \FloatBarrier
+
+    STOP HERE --- A new beginning (this is an upload test).
 

### 2023-09-14 paper.tex
First Draft

@@
 
-    % Please add the following required packages to your document preamble:
-    % \usepackage{booktabs}
-    % \usepackage[table,xcdraw]{xcolor}
-    % If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
     \begin{table}[]
@@
     For each experiment, we ran fifty-one independent executions per CEC-2017 mathematical benchmark function and dimensions specified.
-We recorded the following results: best-found error average, standard deviation, and calculated the statistical Z-Test value.
+We recorded the following results: best-found error average and standard deviation to calculate the statistical Z-Test value.
 The labels used on the results of our summarized results tables are the following:
@@
 
-    To find and determine the best alternative finalized with a statistical Z-Test with a 95 percent confidence level.
-Here are the results statistics values: Table 3 shows the condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions (D) for alternatives One Point and Continuous Range crossover; Table 4 displays the condensed ALCA evaluation results for the CEC-2017 mathematical operations running on thirty D for the same crossover alternatives.
+    To find and determine the best alternative finalized with a statistical Z-Test with a ninety-five percent confidence level.
+Here are the results statistics values: Table~\ref{tab.condensed_evaluation_10D} shows the condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions (D) for alternatives One Point and Continuous Range crossover; Table~\ref{tab.condensed_evaluation_30D} displays the condensed ALCA evaluation results for the CEC-2017 mathematical operations running on thirty D for the same crossover alternatives.
 
-    We performed the statistical Z-Test for both crossover alternatives with a 95 percent confidence level.
-When the One Point passes the test, it is highlighted in green color.
-When the Continuous Range passes the statistical test, it is highlighted in blue.
-Where we did not find enough evidence to declare one choice as the best alternative, no Z value was highlighted.
+    \begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions for alternatives One Point and Continuous Range crossover.}\label{tab.condensed_evaluation_10D}
+    \begin{tabular}{@{}lllllllll@{}}
+    \toprule
+    \multicolumn{9}{c}{\textbf{ALCA . CEC-2017 . 10D}} \\ \midrule
+    Crossover &  & \multicolumn{3}{c}{One Point Xover} &  & \multicolumn{3}{c}{Cont. Range Xover} \\
+    Fx &  & Mean & Std. Dev. & Z &  & Mean & Std. Dev. & Z \\
+    F1 &  & 2.14E+03 & 2.14E+03 & 5.42E+00 &  & 4.43E+02 & 6.46E+02 & \textbf{-5.42E+00} \\
+    F2 &  & 1.81E-03 & 2.63E-03 & 2.38E+00 &  & 8.54E-04 & 1.16E-03 & \textbf{-2.38E+00} \\
+    F3 &  & 4.19E-04 & 1.16E-03 & 2.49E+00 &  & 1.33E-05 & 2.20E-05 & \textbf{-2.49E+00} \\
+    F4 &  & 6.00E+00 & 1.31E+01 & 2.00E+00 &  & 2.31E+00 & 1.78E+00 & \textbf{-2.00E+00} \\
+    F5 &  & 1.53E+01 & 7.06E+00 & 2.45E+00 &  & 1.24E+01 & 4.14E+00 & \textbf{-2.45E+00} \\
+    F6 &  & 6.05E-04 & 9.22E-04 & -1.43E+00 &  & 2.53E-03 & 9.61E-03 & 1.43E+00 \\
+    F7 &  & 3.15E+01 & 9.06E+00 & 2.26E+00 &  & 2.76E+01 & 8.38E+00 & \textbf{-2.26E+00} \\
+    F8 &  & 1.78E+01 & 7.38E+00 & 8.00E+00 &  & 8.62E+00 & 3.53E+00 & \textbf{-8.00E+00} \\
+    F9 &  & 2.02E+01 & 2.24E+01 & 1.85E+00 &  & 1.25E+01 & 1.96E+01 & \textbf{-1.85E+00} \\
+    F10 &  & 4.96E+02 & 2.26E+02 & \textbf{-2.02E+00} &  & 5.94E+02 & 2.63E+02 & 2.02E+00 \\
+    F11 &  & 1.16E+01 & 6.01E+00 & \textbf{-2.44E+00} &  & 1.49E+01 & 7.48E+00 & 2.44E+00 \\
+    F12 &  & 1.70E+04 & 1.99E+04 & 2.00E+00 &  & 1.10E+04 & 8.21E+03 & \textbf{-2.00E+00} \\
+    F13 &  & 7.39E+03 & 8.16E+03 & 1.08E+00 &  & 5.94E+03 & 5.03E+03 & -1.08E+00 \\
+    F14 &  & 3.24E+02 & 6.05E+02 & 4.65E-01 &  & 2.67E+02 & 6.34E+02 & -4.65E-01 \\
+    F15 &  & 5.70E+02 & 1.31E+03 & 1.25E+00 &  & 3.07E+02 & 7.46E+02 & -1.25E+00 \\
+    F16 &  & 1.56E+02 & 1.28E+02 & 5.05E-01 &  & 1.43E+02 & 1.18E+02 & -5.05E-01 \\
+    F17 &  & 3.17E+01 & 3.65E+01 & 1.81E+00 &  & 2.11E+01 & 1.98E+01 & \textbf{-1.81E+00} \\
+    F18 &  & 2.26E+03 & 2.88E+03 & 9.03E-01 &  & 1.73E+03 & 3.06E+03 & -9.03E-01 \\
+    F19 &  & 1.88E+03 & 3.24E+03 & 4.11E-01 &  & 1.63E+03 & 2.95E+03 & -4.11E-01 \\
+    F20 &  & 9.50E+00 & 8.32E+00 & -1.35E+00 &  & 1.20E+01 & 9.92E+00 & 1.35E+00 \\
+    F21 &  & 1.15E+02 & 3.86E+01 & 4.93E-02 &  & 1.15E+02 & 3.58E+01 & -4.93E-02 \\
+    F22 &  & 1.00E+02 & 2.07E+01 & \textbf{-2.57E+00} &  & 1.08E+02 & 8.70E+00 & 2.57E+00 \\
+    F23 &  & 3.21E+02 & 7.31E+00 & \textbf{-2.53E+00} &  & 3.25E+02 & 8.91E+00 & 2.53E+00 \\
+    F24 &  & 3.28E+02 & 8.06E+01 & 5.36E+00 &  & 2.15E+02 & 1.28E+02 & \textbf{-5.36E+00} \\
+    F25 &  & 4.35E+02 & 2.61E+01 & 1.39E+00 &  & 4.28E+02 & 2.41E+01 & -1.39E+00 \\
+    F26 &  & 3.99E+02 & 1.25E+02 & 7.55E-01 &  & 3.82E+02 & 9.35E+01 & -7.55E-01 \\
+    F27 &  & 3.88E+02 & 1.03E+01 & -5.43E-01 &  & 3.90E+02 & 1.13E+01 & 5.43E-01 \\
+    F28 &  & 4.11E+02 & 7.92E+01 & 1.93E+00 &  & 3.80E+02 & 8.46E+01 & \textbf{-1.93E+00} \\
+    F29 &  & 3.00E+02 & 4.32E+01 & 7.44E-01 &  & 2.94E+02 & 3.30E+01 & -7.44E-01 \\
+    F30 &  & 3.21E+02 & 1.52E+02 & -7.14E-01 &  & 3.44E+02 & 1.81E+02 & 7.14E-01 \\
+    \textbf{Total (W)} &  & \multicolumn{2}{c}{\textbf{One Point Xover}} & \multicolumn{1}{c}{\textbf{4 of 30}} &  & \multicolumn{2}{c}{\textbf{Cont.
+Range Xover}} & \multicolumn{1}{c}{\textbf{12 of 30}} \\ \bottomrule
+    \end{tabular}
+    \end{table}
 
@@
 
-    STOP HERE --- A new beginning (this is an upload test).
+    We performed the statistical Z-Test for both crossover alternatives with a 95 percent confidence level.
+When the One Point passes the test, the Z value is highlighted in bold on the left column.
+When the Continuous Range passes the statistical test, the Z value is highlighted in bold on the right column.
+Where we did not find enough evidence to declare one choice as the best alternative, no value was highlighted.
 
-    Imagine being an astronaut on a mission repairing a space station in the
-    middle of space. Suddenly, a block of asteroids hits the craft, and you
-    lose your oxygen tank while the explosion pushes you away. From afar, you
-    see the area where your tank might be, covered with something similar to a
-    gas leaked from the station that blocks all visibility. Finding the tank is
-    the only hope to return to your main ship some miles away. The oxygen
-    reserve from your suit is running out, and there are only a couple of
-    minutes left. Now hold your breath in real life and think, what strategy
-    will you choose to search for your tank? We repeated this mental exercise
-    several times until we found the best solution (or blacked out).
+    \begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Condensed ALCA evaluation results for the CEC-2017 functions running on thirty dimensions for alternatives One Point and Continuous Range crossover.}\label{tab.condensed_evaluation_30D}
+    \begin{tabular}{@{}lllllllll@{}}
+    \toprule
+    \multicolumn{9}{c}{\textbf{ALCA . CEC-2017 . 30D}} \\ \midrule
+    Crossover &  & \multicolumn{3}{c}{One Point Xover} &  & \multicolumn{3}{c}{Cont. Range Xover} \\
+    Fx &  & Mean & Std. Dev. & Z &  & Mean & Std. Dev. & Z \\
+    F1 &  & 4.92E+03 & 6.21E+03 & 1.60E+00 &  & 3.35E+03 & 3.33E+03 & -1.60E+00 \\
+    F2 &  & 9.21E+06 & 4.77E+07 & 1.37E+00 &  & 6.96E+04 & 2.50E+05 & -1.37E+00 \\
+    F3 &  & 1.17E+02 & 1.18E+02 & 4.33E+00 &  & 4.16E+01 & 3.85E+01 & \textbf{-4.33E+00} \\
+    F4 &  & 7.17E+01 & 3.14E+01 & -5.29E-01 &  & 7.46E+01 & 2.52E+01 & 5.29E-01 \\
+    F5 &  & 9.38E+01 & 2.41E+01 & 4.61E-01 &  & 9.18E+01 & 2.04E+01 & -4.61E-01 \\
+    F6 &  & 4.67E-03 & 1.02E-02 & \textbf{-2.42E+00} &  & 2.28E-02 & 5.26E-02 & 2.42E+00 \\
+    F7 &  & 1.55E+02 & 3.04E+01 & -3.88E-01 &  & 1.58E+02 & 3.44E+01 & 3.88E-01 \\
+    F8 &  & 9.94E+01 & 2.43E+01 & 6.82E+00 &  & 7.29E+01 & 1.32E+01 & \textbf{-6.82E+00} \\
+    F9 &  & 1.37E+03 & 7.21E+02 & 4.60E+00 &  & 8.19E+02 & 4.64E+02 & \textbf{-4.60E+00} \\
+    F10 &  & 2.79E+03 & 5.59E+02 & \textbf{-2.22E+00} &  & 3.02E+03 & 4.63E+02 & 2.22E+00 \\
+    F11 &  & 7.31E+01 & 2.72E+01 & -1.09E+00 &  & 7.90E+01 & 2.75E+01 & 1.09E+00 \\
+    F12 &  & 2.18E+05 & 1.94E+05 & 4.61E+00 &  & 8.73E+04 & 5.95E+04 & \textbf{-4.61E+00} \\
+    F13 &  & 1.95E+04 & 2.73E+04 & 2.09E+00 &  & 1.10E+04 & 8.96E+03 & \textbf{-2.09E+00} \\
+    F14 &  & 2.22E+04 & 2.14E+04 & 2.83E+00 &  & 1.27E+04 & 1.06E+04 & \textbf{-2.83E+00} \\
+    F15 &  & 1.25E+04 & 1.41E+04 & 4.96E+00 &  & 2.37E+03 & 3.82E+03 & \textbf{-4.96E+00} \\
+    F16 &  & 1.26E+03 & 3.45E+02 & 1.49E-01 &  & 1.26E+03 & 2.49E+02 & -1.49E-01 \\
+    F17 &  & 6.02E+02 & 1.76E+02 & 1.17E+00 &  & 5.54E+02 & 2.36E+02 & -1.17E+00 \\
+    F18 &  & 1.29E+05 & 1.17E+05 & 2.92E+00 &  & 7.44E+04 & 6.27E+04 & \textbf{-2.92E+00} \\
+    F19 &  & 9.78E+03 & 1.16E+04 & 3.04E+00 &  & 4.38E+03 & 5.08E+03 & \textbf{-3.04E+00} \\
+    F20 &  & 4.83E+02 & 1.69E+02 & 1.02E-01 &  & 4.79E+02 & 2.03E+02 & -1.02E-01 \\
+    F21 &  & 3.03E+02 & 2.44E+01 & 4.40E+00 &  & 2.85E+02 & 1.62E+01 & \textbf{-4.40E+00} \\
+    F22 &  & 1.76E+03 & 1.72E+03 & 6.07E+00 &  & 2.16E+02 & 5.84E+02 & \textbf{-6.07E+00} \\
+    F23 &  & 4.62E+02 & 3.06E+01 & \textbf{-5.27E+00} &  & 5.05E+02 & 4.97E+01 & 5.27E+00 \\
+    F24 &  & 6.45E+02 & 7.43E+01 & \textbf{-2.31E+00} &  & 6.78E+02 & 7.03E+01 & 2.31E+00 \\
+    F25 &  & 3.85E+02 & 1.49E+01 & \textbf{-3.06E+00} &  & 3.97E+02 & 2.40E+01 & 3.06E+00 \\
+    F26 &  & 2.40E+03 & 4.88E+02 & -1.23E+00 &  & 2.61E+03 & 1.17E+03 & 1.23E+00 \\
+    F27 &  & 4.94E+02 & 1.23E+01 & 2.98E-01 &  & 4.93E+02 & 1.95E+01 & -2.98E-01 \\
+    F28 &  & 4.63E+02 & 4.29E+01 & 9.26E+00 &  & 3.98E+02 & 2.58E+01 & \textbf{-9.26E+00} \\
+    F29 &  & 9.22E+02 & 2.36E+02 & 1.55E+00 &  & 8.56E+02 & 2.00E+02 & -1.55E+00 \\
+    F30 &  & 3.53E+03 & 4.15E+03 & 4.09E+00 &  & 1.08E+03 & 1.04E+03 & \textbf{-4.09E+00} \\
+    \multicolumn{1}{c}{\textbf{Total (W)}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{One Point Xover}} & \multicolumn{1}{c}{\textbf{5 of 30}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Cont.
+Range Xover}} & \multicolumn{1}{c}{\textbf{13 of 30}} \\ \bottomrule
+    \end{tabular}
+    \end{table}
 
-    If your life depended on it, would you choose a Genetic Algorithm, a
-    variant of a Particle Swarm Optimization Algorithm, or another? We searched
-    for a way to mix both, at least in some way, take the main idea or concepts
-    from them and make them work together. We strongly believe it is possible
-    to combine the features, as previous work has proven to obtain outstanding
-    results \cite{garcia2015evospace,garcia2021event,valdez2021container,valdez2021swarm}.
-    Our goal was to create a swarm out of the best individuals found in
-    evolution. We probably have a long way to go, but at least we are getting
-    promising results. From our experiments, all six Classic Benchmark
-    Functions for Optimization (Ackley, Bohachevsky, Griewank, Rastrigin,
-    Sphere, and Rosenbrock) proved the same behavior for the Animal Life Cycle
-    Algorithm: finding the expected solution in a reduced number of evaluations
-    and less execution time.
+    \FloatBarrier
 
@@
 
-    The Animal Life Cycle Algorithm allows for multiple parameters'
-    fine-tuning, facilitating the freedom to experiment with different
-    alternatives to restart the population and solve extinction caused by
-    nature's pressure, which will impact how quickly, and the quality of its
-    found solution. We compared the results obtained with the use of historical
-    elite projection versus other alternatives, using classic benchmark
-    functions for optimization for comparison, where it showed favorable and
-    promising results.
+    To validate our research, we performed the statistical Z-Test with a ninety-five percent confidence level to analyze the alternatives we present in this proposal.
+In the ten-dimension category, we found that One Point crossover was the better alternative on four occasions, while our Continuous Range proposal was better on twelve other functions out of thirty.
+For the thirty-dimensions category, the One Point crossover was better on five occasions, while the Continuous Range crossover was the best alternative on another thirteen.
+Our experiment results confirm that our solution can be considered a good alternative.
 
-    As the nature of the challenge increases, it is indispensable to have an
-    elastic, scalable, and fault-tolerant model designed with cloud
-    collaboration processes, and asynchronous communication. We have proven
-    that it is possible to evolve a population, using a distributed, parallel,
-    and asynchronous strategy, inspired by the Genetic Algorithm (GA). To
-    further validate this work, we could use some more demanding (or control)
-    problem that requires calculating real numbers
-    \cite{stanley2002evolving,miikkulainen2019evolving}. We implemented the
-    algorithm using Docker containers.
+    Some researchers might consider our proposal similar to what is used by algorithms such as Differential Evolution, where we think of our proposal as a variation of existing proposals because we expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals.
+Experimental results indicate that our proposed operator may be a good alternative for the canonical One Point crossover.
 

### 2023-09-20 paper.tex
Turnitin improvement A.

@@
 
-\titlerunning{Animal Life Cycle Algorithm (ALCA)}
+\titlerunning{A new breeding crossover approach for evolutionary algorithms}
 % Use \titlerunning{Short Title} for an abbreviated version of
@@
 \abstract*{In a previous work, we introduced a population-based, bio-inspired algorithm.
-The proposed algorithm is inspired by the biological animal life cycle, consisting of the stages of birth, growth, reproduction, and death.
+The proposed algorithm is inspired by the biological animal life cycle, consisting of the birth, growth, reproduction, and death stages.
 Our algorithm was initially based on the canonical Genetic Algorithm (GA), where all the individuals have a genotype (chromosome).
@@
 We expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals.
-In this paper, we use the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC2017) to compare the traditional one-point crossover and our proposed strategy.
+This paper uses the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC2017) to compare the traditional one-point crossover and our proposed strategy.
 Experimental results indicate that our proposed operator may be a good alternative for the canonical crossover.}
@@
 \abstract{In a previous work, we introduced a population-based, bio-inspired algorithm.
-The proposed algorithm is inspired by the biological animal life cycle, consisting of the stages of birth, growth, reproduction, and death.
+The proposed algorithm is inspired by the biological animal life cycle, consisting of the birth, growth, reproduction, and death stages.
 Our algorithm was initially based on the canonical Genetic Algorithm (GA), where all the individuals have a genotype (chromosome).
@@
     Biologically inspired algorithms are a very effective technique to solve complex optimization problems\cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}.
-Traditionally, nature-inspired algorithms are developed with a sequential perspective\cite{porto2018evolutionary,back1996evolutionary},  meaning that all tasks execute one step at a time, where all processes must wait for the previous to finish before continuing (synchronous perspective).
-Some architectures address this issue by working on the cloud\cite{valdez2021container,garcia2015evospace,merelo2016nodio} and finding solutions on distributed technologies.
+Traditionally, nature-inspired algorithms are developed with a sequential perspective\cite{porto2018evolutionary,back1996evolutionary}, meaning that all tasks execute one step at a time, where all processes must wait until the current task finishes before proceeding (synchronous perspective).
+One solution to this issue is working with cloud computing\cite{valdez2021container,garcia2015evospace,merelo2016nodio} and using distributed architectures.
 
     In previous work, we introduced a population-based, bio-inspired algorithm\cite{Felix-Saul2022,Felix-Saul2023}.
-The proposed algorithm is inspired by the biological animal life cycle, consisting of the stages\cite{read1968system} of birth, growth, reproduction, and death.
-Our algorithm was initially based on the canonical Genetic Algorithm (GA)\cite{holland1992genetic,holland1984genetic}, where all the individuals have a genotype (chromosome).
-Our algorithm’s goal is to mimic the animal life cycle, where at any given moment, new individuals are born to be part of the population and participate in the collective evolution.
-As time passes, they grow older and mature, suffering changes throughout their lives that we chose to represent as mutations.
+The proposed algorithm is inspired by the biological animal life cycle, consisting of the birth, growth, reproduction, and death stages\cite{read1968system}.
+Our algorithm was initially based on the canonical Genetic Algorithm (GA)\cite{holland1992genetic,holland1984genetic}, where all the individuals have a genotype (chromosome) constructed by a list of values, where we compute the individual's fitness using an evaluation function that represents the problem we wish to solve.
 
-    In our analysis, we thought of death’s work to maintain balance in the population by enforcing the survival of the fittest.
-As in life, death can happen to everyone: from a newborn to the elderly, where fitness will determine the individual’s longevity.
-This algorithm was inspired by the traditional Genetic Algorithm \cite{holland1992genetic,holland1984genetic}, meaning that all individuals have a genotype (chromosome) that is a list of values.
-We calculate the individual’s fitness with the evaluation function and do crossover and mutation to the population.
+    The algorithm's main objective is to abstract how the animal life cycle performs in nature, where at any given time, newborn individuals are integrated into the population and partake in communal evolution.
+Progressively, all individuals grow and mature, consequently suffering changes that we represent with mutations in our design.
+In our modeling, we enforced the survival of the fittest.
+As in nature, death randomly tests every living organism to help maintain balance in the numbers in the population; therefore, it is independent of the individual's age.
+However, fitness will be the main factor in prolonging its longevity.
 
-    What makes our strategy different is that we don’t use the concept of evolutionary generations.
-We manage our set of solutions as a whole that continuously evolve over time.
-Allowing individuals of different ages to breed and generate offspring, as it happens in nature.
-One difference to highlight in our algorithm is that both the crossover (reproduction) and mutation (growth) are executed through independent processes that randomly affect the population.
-We display the general model concept for the Animal Life Cycle Algorithm (ALCA) in Figure~\ref{fig.algorithm_model}.
+    One essential feature to highlight in the algorithm is that it doesn't use the concept of generations in the evolution.
+Our strategy views the population as a set of candidate solutions that evolve continuously over time, which allows individuals of multiple ages to reproduce and generate new offspring, reflecting nature's actual behavior.
+Another difference to highlight in our algorithm is that both reproduction (crossover) and growth (mutation) execute through independent processes that randomly affect the population.
+Figure~\ref{fig.algorithm_model} displays the general model concept for the Animal Life Cycle Algorithm (ALCA).
 
-    In this research, we propose a new alternative for reproduction, a new breeding crossover approach for evolutionary algorithms using the classic one-point crossover as a reference to our proposal.
+    We propose a new reproduction alternative in this research: a new breeding crossover approach for evolutionary algorithms using the classic one-point crossover as a reference to our proposal.
 We performed comparison experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) for evaluation.
-We finalize with a statistical Z-Test with a 95 percent confidence level to determine the best alternative.
+We finalize with a statistical Z-Test with a ninety-five percent confidence level to determine the best alternative.
 
@@
 First, we illustrate our alternative crossover proposal, from the inspiration to a detailed example.
-We compare the canonical one-point crossover with our proposed solution in section~\ref{section.proposal}, followed by our experiment configuration and results in section~\ref{section.experiments}, where we analyze and describe some of our research findings in section~\ref{section.discussion}.
-We finalize by presenting some inferences based on the results of our experiments in section~\ref{section.conclusions}.
+The proposal section~\ref{section.proposal} compares the canonical one-point crossover with our crossover solution.
+We continue with the experiments section~\ref{section.experiments} with our experiment configuration and results.
+We include the analysis and description of some of our research discoveries in the discussion section~\ref{section.discussion}.
+The conclusions section~\ref{section.conclusions} finalizes presenting some deductions founded on the study of our experiments.
 
@@
 
-    Let's imagine that colors black and white fell in love and had beautiful children.
+    Let's imagine that the colors black and white fell in love and had children.
 If we had to guess what color their offspring would be, it could only be predictable its children's color would be inside the domain shown in Figure~\ref{fig.grayscale_continuous}.
@@
         \includegraphics[width=0.70\linewidth]{img/fig_grayscale_continuous.pdf}
-        \caption{Black and white offspring predictable color domain.} \label{fig.grayscale_continuous}
+        \caption{Black and white offspring, predictable color domain.} \label{fig.grayscale_continuous}
         \end{figure}
 
-    If we replace colors black and white with values 0 and 1 respectively, how many values can we find in between?
+    If we replace the colors black and white with values 0 and 1, respectively, how many values can we find in between?
 We could replace attributes, switching from color to height, strength, agility, or any other feature we might need to focus on.
@@
 
-    In this paper, we propose a different alternative to the classical approach, where part of the genetic information is directly copied to each of the offspring in the crossover operator, where this type of crossover may not perform well in continuous optimization problems.
-We provide an example of the One Point Crossover in Figure~\ref{fig.onepoint_crossover}.
+    In this document, we propose a different technique to the canonical approach One Point Crossover, where part of the genetic information is copied directly to each of the offspring in the crossover operator, where this type of crossover may perform inadequately in continuous optimization problems.
+Figure~\ref{fig.onepoint_crossover} provides an example of the One Point Crossover.
 
@@
     We used the Animal Life Cycle Algorithm (ALCA) for our experiments, switching between the breeding strategies (One Point and Continuous Range Crossover) with the same general setup.
-In Table~\ref{tab.general_configuration}, we can find the General Configuration used to run the experiments for our research, where all values from this configuration remained constant during all phases of the experiment runs.
+Table~\ref{tab.general_configuration} displays the General Configuration used to run the experiments for our research, where all the values remained consistent during all the stages of the test runs.
 
@@
 
-    For each experiment, we ran fifty-one independent executions per CEC-2017 mathematical benchmark function and dimensions specified.
-We recorded the following results: best-found error average and standard deviation to calculate the statistical Z-Test value.
-The labels used on the results of our summarized results tables are the following:
+    For our experimentation, we executed fifty-one independent runs per specified dimension for each CEC-2017 mathematical benchmark function.
+We registered the following values: best-found error average and standard deviation to calculate the statistical Z-Test value.
+We summarized our results in the following tables, with the labels described next:
 
@@
         \item   Fx:          is the mathematical benchmark function.
-        \item   Mean:        is the best-found error average.
-        \item   St-Dev:      is the standard deviation calculated from the error. 
+        \item   Mean:        is the average of the best-found error.
+        \item   St-Dev:      is the computed error standard deviation. 
         \item   Z:           is the calculated statistical Z-Test value.
@@
 
-    To find and determine the best alternative finalized with a statistical Z-Test with a ninety-five percent confidence level.
-Here are the results statistics values: Table~\ref{tab.condensed_evaluation_10D} shows the condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions (D) for alternatives One Point and Continuous Range crossover; Table~\ref{tab.condensed_evaluation_30D} displays the condensed ALCA evaluation results for the CEC-2017 mathematical operations running on thirty D for the same crossover alternatives.
+    To find and determine the best alternative, finalized with a statistical Z-Test with a ninety-five percent confidence level.
+Here are the results' statistics values: Table~\ref{tab.condensed_evaluation_10D} shows the condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions (D) for alternatives One Point and Continuous Range crossover; Table~\ref{tab.condensed_evaluation_30D} displays the condensed ALCA evaluation results for the CEC-2017 mathematical operations running on thirty D for the same crossover alternatives.
 
@@
 For the thirty-dimensions category, the One Point crossover was better on five occasions, while the Continuous Range crossover was the best alternative on another thirteen.
-Our experiment results confirm that our solution can be considered a good alternative.
+Our experiment results confirm that our solution can be considered a adequate alternative.
 
-    Some researchers might consider our proposal similar to what is used by algorithms such as Differential Evolution, where we think of our proposal as a variation of existing proposals because we expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals.
-Experimental results indicate that our proposed operator may be a good alternative for the canonical One Point crossover.
+    Some researchers might consider our proposal similar to what is used by algorithms such as Differential Evolution, where we consider our proposal to be a variation of existing proposals because we expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals.
+Experimental results indicate that our proposed operator may be a viable alternative for the canonical One Point crossover.
 

### 2023-09-20 paper.tex
Conclusion Update

@@
 
+    One of the most important contributions of this research is that it proposes a new crossing alternative for the reproduction of individuals in a population.
+This strategy is practical in evolutionary algorithms where the individual's information has a structure similar to the genetic code's.
+With some tinkering, this strategy could be valuable in other algorithms\cite{venter2003particle,wang2018particle}, such as Particle Swarm Optimization (PSO).
+
     We organized this paper in the following structure.
@@
 
-    In this document, we propose a different technique to the canonical approach One Point Crossover, where part of the genetic information is copied directly to each of the offspring in the crossover operator, where this type of crossover may perform inadequately in continuous optimization problems.
+    In this document, we propose a different technique to the canonical approach One Point Crossover, where part of the genetic information is copied directly to each offspring in the crossover operator.
+This type of crossover may fail to perform successfully in continuous optimization problems.
 Figure~\ref{fig.onepoint_crossover} provides an example of the One Point Crossover.
@@
         \centering
-        \includegraphics[width=0.70\linewidth]{img/fig_onepoint_crossover.pdf}
+        \includegraphics[width=0.50\linewidth]{img/fig_onepoint_crossover.pdf}
         \caption{Classical approach example for the One Point Crossover, with crossover point 3.} \label{fig.onepoint_crossover}
@@
         \centering
-        \includegraphics[width=0.70\linewidth]{img/fig_contrange_crossover.pdf}
+        \includegraphics[width=0.50\linewidth]{img/fig_contrange_crossover.pdf}
         \caption{Our proposal example for the Continuous Range Crossover mating the same couple of individuals.} \label{fig.contrange_crossover}
@@
 For the thirty-dimensions category, the One Point crossover was better on five occasions, while the Continuous Range crossover was the best alternative on another thirteen.
-Our experiment results confirm that our solution can be considered a adequate alternative.
+Our experiment results confirm that our solution can be considered an adequate alternative.
 
@@
 
+    Based on the analysis of our results, we have shown that the proposed crossover alternative for the reproduction of individuals in a population obtains good results.
+Therefore, it can be valuable in other evolutionary algorithms where the information of individuals has a structure similar to that of the genetic code.
+However, with some adaptation, it could be helpful in different types of algorithms, such as Particle Swarm Optimization.
+In future work, we could investigate a combination between the canonical One Point Crossover strategy and randomly alternating with the proposed Continuous Range Crossover.
+
 \begin{acknowledgement}
-    This paper has been supported in part by TecNM Project 15340.22-P.
+    This paper has been supported in part by TecNM Project 18186.23-P.
 \end{acknowledgement}

### 2023-09-20 paper.tex
Figure Enlargement

@@
 Another difference to highlight in our algorithm is that both reproduction (crossover) and growth (mutation) execute through independent processes that randomly affect the population.
-Figure~\ref{fig.algorithm_model} displays the general model concept for the Animal Life Cycle Algorithm (ALCA).
+Figure~\ref{fig.algorithm_model} displays the general model concept for the Animal Life Cycle Algorithm (ALCA)\cite{Felix-Saul2023}.
 
@@
         \includegraphics[width=0.90\linewidth]{img/fig_algorithm_model.pdf}
-        \caption{Animal Life Cycle Algorithm model.} \label{fig.algorithm_model}
+        \caption{Animal Life Cycle Algorithm model\cite{Felix-Saul2023}.} \label{fig.algorithm_model}
         \end{figure}
@@
         \centering
-        \includegraphics[width=0.70\linewidth]{img/fig_grayscale_continuous.pdf}
+        \includegraphics[width=0.90\linewidth]{img/fig_grayscale_continuous.pdf}
         \caption{Black and white offspring, predictable color domain.} \label{fig.grayscale_continuous}
@@
         \centering
-        \includegraphics[width=0.50\linewidth]{img/fig_onepoint_crossover.pdf}
+        \includegraphics[width=0.90\linewidth]{img/fig_onepoint_crossover.pdf}
         \caption{Classical approach example for the One Point Crossover, with crossover point 3.} \label{fig.onepoint_crossover}
@@
         \centering
-        \includegraphics[width=0.50\linewidth]{img/fig_contrange_crossover.pdf}
+        \includegraphics[width=0.90\linewidth]{img/fig_contrange_crossover.pdf}
         \caption{Our proposal example for the Continuous Range Crossover mating the same couple of individuals.} \label{fig.contrange_crossover}
@@
 \begin{acknowledgement}
-    This paper has been supported in part by TecNM Project 18186.23-P.
+    TecNM Project 18186.23-P has partially funded this research.
 \end{acknowledgement}

### 2023-09-20 paper.tex
Result Tables Update

@@
 Our strategy views the population as a set of candidate solutions that evolve continuously over time, which allows individuals of multiple ages to reproduce and generate new offspring, reflecting nature's actual behavior.
-Another difference to highlight in our algorithm is that both reproduction (crossover) and growth (mutation) execute through independent processes that randomly affect the population.
+Another difference to highlight in our algorithm is that both reproduction (crossover) and growth (mutation) execute through autonomous processes that interact with the population randomly.
 Figure~\ref{fig.algorithm_model} displays the general model concept for the Animal Life Cycle Algorithm (ALCA)\cite{Felix-Saul2023}.
@@
         \hfill
-        \vspace{0.05 cm}
         \begin{minipage}[h]{0.49\linewidth}
@@
         \end{minipage}
-
-        \caption{Box and Whisker charts for mathematical functions F1 and F2.
-We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F1-F2}
-    \end{figure}
-
-    \FloatBarrier
-
-    \begin{figure}[!ht]
+        \vfill
+        \vspace{0.05 cm}
         \begin{minipage}[h]{0.49\linewidth}
@@
         \end{minipage}
-        \vfill
-        \vspace{0.05 cm}
+
+        \caption{Box and Whisker charts for mathematical functions F1 to F5.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F1-F5}
+    \end{figure}
+
+    \FloatBarrier
+
+    \begin{figure}[!ht]
         \begin{minipage}[h]{0.49\linewidth}
@@
         \end{minipage}
-
-        \caption{Box and Whisker charts for mathematical functions F3 to F8.
-We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F3-F8}
-    \end{figure}
-
-    \FloatBarrier
-
-    \begin{figure}[!ht]
+        \vfill
+        \vspace{0.05 cm}
         \begin{minipage}[h]{0.49\linewidth}
@@
         \end{minipage}
-        \vfill
-        \vspace{0.05 cm}
+
+        \caption{Box and Whisker charts for mathematical functions F6 to F10.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F6-F10}
+    \end{figure}
+
+    \FloatBarrier
+
+    \begin{figure}[!ht]
         \begin{minipage}[h]{0.49\linewidth}
@@
         \end{minipage}
-
-        \caption{Box and Whisker charts for mathematical functions F9 to F14.
-We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F9-F14}
-    \end{figure}
-
-    \FloatBarrier
-
-    \begin{figure}[!ht]
+        \vfill
+        \vspace{0.05 cm}
         \begin{minipage}[h]{0.49\linewidth}
@@
         \end{minipage}
-        \vfill
-        \vspace{0.05 cm}
+
+        \caption{Box and Whisker charts for mathematical functions F11 to F15.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F11-F15}
+    \end{figure}
+
+    \FloatBarrier
+
+    \begin{figure}[!ht]
         \begin{minipage}[h]{0.49\linewidth}
@@
 
-        \caption{Box and Whisker charts for mathematical functions F15 to F20.
-We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F15-F20}
+        \caption{Box and Whisker charts for mathematical functions F16 to F20.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F16-F20}
     \end{figure}
@@
         \end{minipage}
-        \vfill
-        \vspace{0.05 cm}
+
+        \caption{Box and Whisker charts for mathematical functions F21 to F25.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F21-F25}
+    \end{figure}
+
+    \FloatBarrier
+
+    \begin{figure}[!ht]
         \begin{minipage}[h]{0.49\linewidth}
@@
         \end{minipage}
-
-        \caption{Box and Whisker charts for mathematical functions F21 to F26.
-We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F21-F26}
-    \end{figure}
-
-    \FloatBarrier
-
-    \begin{figure}[!ht]
+        \vfill
+        \vspace{0.05 cm}
         \begin{minipage}[h]{0.49\linewidth}
@@
 
-        \caption{Box and Whisker charts for mathematical functions F27 to F30.
-We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F27-F30}
+        \caption{Box and Whisker charts for mathematical functions F26 to F30.
+We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F26-F30}
     \end{figure}

### 2023-09-21 paper.tex
Proposal update

@@
         \centering
-        \includegraphics[width=0.90\linewidth]{img/fig_grayscale_continuous.pdf}
+        \includegraphics[width=0.80\linewidth]{img/fig_grayscale_continuous.pdf}
         \caption{Black and white offspring, predictable color domain.} \label{fig.grayscale_continuous}
@@
 Our proposal example for the Continuous Range Crossover is displayed in Figure~\ref{fig.contrange_crossover}, where it should be noted that we construct a template that will be used for all the offspring generated by each couple.
+
+    An exciting functionality of this strategy is that this new crossover operation will enable the offspring to continue exploring new search spaces with the birth of unique individuals.
+Because of the new values obtained within the parent's chromosome ranges, this technique will be helpful to avoid local optima stagnation by maintaining diversity due to the near-infinite possibility of stochastic values.
+
+    Our proposed strategy is beneficial for evolutionary algorithms, where the individual's genetic code (or a similar data layout) is the main structure for storing the population information.
+It could also be valuable for other algorithms, such as Particle Swarm Optimization (PSO), in computing the new placement position caused by the movement of the particles.
 

### 2023-09-21 paper.tex
Proposal Update 2

@@
     \FloatBarrier
+
+    As shown in Figure~\ref{fig.contrange_crossover}, Continuous Range Crossover, we generate a template with the chromosome values of the parents.
+We use this template for the generation of all their children.
+In the following experiment results shown in this document, we have generated two children per couple reproduction, the same way the One Point Crossover strategy does.
+This offspring number generated has the purpose of maintaining a balance in the population created by the reproduction operator in both proposals.
 

### 2023-09-21 paper.tex
General Updates

@@
 The proposed algorithm is inspired by the biological animal life cycle, consisting of the birth, growth, reproduction, and death stages\cite{read1968system}.
-Our algorithm was initially based on the canonical Genetic Algorithm (GA)\cite{holland1992genetic,holland1984genetic}, where all the individuals have a genotype (chromosome) constructed by a list of values, where we compute the individual's fitness using an evaluation function that represents the problem we wish to solve.
+Our algorithm was initially based on the canonical Genetic Algorithm (GA)\cite{holland1992genetic,holland1984genetic}, where the individual genotype design is defined by a set of values (chromosome).
+We compute each individual's fitness using a mathematical evaluation function representing the problem we wish to solve.
 
@@
 Our strategy views the population as a set of candidate solutions that evolve continuously over time, which allows individuals of multiple ages to reproduce and generate new offspring, reflecting nature's actual behavior.
-Another difference to highlight in our algorithm is that both reproduction (crossover) and growth (mutation) execute through autonomous processes that interact with the population randomly.
+Another difference to highlight in our algorithm is that both reproduction (crossover) and growth (mutation) execute through autonomous processes that interact with the population stochastically.
 Figure~\ref{fig.algorithm_model} displays the general model concept for the Animal Life Cycle Algorithm (ALCA)\cite{Felix-Saul2023}.

### 2023-09-21 paper.tex
Functions Description 1 to 5

@@
 The closer the error results get to the zero value, the better.
+Below, we describe Figure~\ref{fig.experiment_F1-F5}, which includes Functions 1 to 5 (F1 to F5).
+
+    \begin{itemize}
+        \item In function F1 for the ten-dimensional category, the Continuous Range Crossover (CRx) methodology outperformed the One Point Crossover (OPx) methodology in the statistical test.
+We needed to find more evidence for the thirty dimensions category to determine whether any crossover alternative would be better.
+        \item For function F2 for the category of 10 dimensions, again, the CRx strategy outperformed the alternative approach OPx in the statistical test.
+More evidence was required for the thirty dimensions category to declare any of them as the best.
+        \item For function F3 for both categories, 10 and 30 dimensions, the statistical test found better results for our proposed CRx strategy than the alternative OPx.
+        \item For function F4, only for the 10-dimensional category, the CRx strategy proved to be better through the statistical test, while for the 30-dimensional variety, it could not identify any of them as the best.
+        \item For function F5, only for the 10-dimensional category, the proposed strategy CRx passed the statistical test to its alternative OPx, while for the 30-dimensional type, they obtained similar results.
+    \end{itemize}
 

### 2023-09-21 paper.tex
Functions F6 to F10 update.

@@
         \item For function F5, only for the 10-dimensional category, the proposed strategy CRx passed the statistical test to its alternative OPx, while for the 30-dimensional type, they obtained similar results.
+    \end{itemize}
+
+    Below, we describe the results shown in Figure~\ref{fig.experiment_F6-F10}, which includes Functions 6 through 10 (F6 to F10).
+
+    \begin{itemize}
+        \item In function F6 for the category of 10 dimensions, there was not enough evidence to determine that any of the proposals were better, while for the variety of 30, for the first occasion, the OPx alternative surpassed our CRx proposal in the statistical test.
+        \item For function F7, for the category of 10 dimensions, once again, the CRx strategy outperforms its alternative through the statistical test, while for the 30-dimension type, we found not enough evidence to declare any of them as the best proposal.
+        \item For function F8, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
+        \item For function F9, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
+        \item For function F10, the opposite of the previous function occurred, where for both dimensions, 10 and 30, the classic OPx strategy obtained better results than our CRx proposal by passing the statistical test in both cases.
     \end{itemize}

### 2023-09-21 paper.tex
Functions F1 to F10 update

--- 2023-09-21 paper.tex
@@
 The closer the error results get to the zero value, the better.
+Below, we describe Figure~\ref{fig.experiment_F1-F5}, which includes Functions 1 to 5 (F1 to F5).
+
+    \begin{itemize}
+        \item In function F1 for the ten-dimensional category, the Continuous Range Crossover (CRx) methodology outperformed the One Point Crossover (OPx) methodology in the statistical test.
+We needed to find more evidence for the thirty dimensions category to determine whether any crossover alternative would be better.
+        \item At function F2 for the category of 10 dimensions, again, the CRx strategy outperformed the alternative approach OPx in the statistical test.
+More evidence was required for the thirty dimensions category to declare any of them as the best.
+        \item At function F3 for both categories, 10 and 30 dimensions, the statistical test found better results for our proposed CRx strategy than the alternative OPx.
+        \item At function F4, only for the 10-dimensional category, the CRx strategy proved to be better through the statistical test, while for the 30-dimensional variety, it could not identify any of them as the best.
+        \item At function F5, only for the 10-dimensional category, the proposed strategy CRx passed the statistical test to its alternative OPx, while for the 30-dimensional type, they obtained similar results.
+    \end{itemize}
+
+    We describe the results shown in Figure~\ref{fig.experiment_F6-F10}, including functions F6 through F10.
+
+    \begin{itemize}
+        \item In function F6, for the category of 10 dimensions, there needed to be more evidence to determine that any of the proposals were best.
+For the variety of 30, the OPx alternative surpassed our CRx proposal in the statistical test for the first occasion.
+        \item At function F7, for the category of 10 dimensions, once again, the CRx strategy outperforms its alternative through the statistical test.
+For the 30-dimension type, we found not enough evidence to declare any of them as the best proposal.
+        \item At function F8, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
+        \item At function F9, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
+        \item At function F10, the opposite of the previous function occurred, where for both dimensions, 10 and 30, the classic OPx strategy obtained better results than our CRx proposal by passing the statistical test in both cases.
+    \end{itemize}
 

### 2023-09-21 paper.tex
Functions F1 to F12 update.

@@
         \item At function F4, only for the 10-dimensional category, the CRx strategy proved to be better through the statistical test, while for the 30-dimensional variety, it could not identify any of them as the best.
-        \item At function F5, only for the 10-dimensional category, the proposed strategy CRx passed the statistical test to its alternative OPx, while for the 30-dimensional type, they obtained similar results.
+        \item At function F5, only for the 10-dimensional category, the proposed strategy CRx passed the statistical test compared to its alternative OPx, while for the 30-dimensional type, they obtained similar results.
     \end{itemize}
@@
         \item At function F10, the opposite of the previous function occurred, where for both dimensions, 10 and 30, the classic OPx strategy obtained better results than our CRx proposal by passing the statistical test in both cases.
+    \end{itemize}
+
+    We describe the results shown in Figure~\ref{fig.experiment_F11-F15}, including functions F11 through F15.
+
+    \begin{itemize}
+        \item At function F11, only for the 10-dimensional category, the original OPx passed the statistical test compared to our proposed strategy CRx, while for the 30-dimensional type, they obtained similar results.
+        \item At function F12, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
+
     \end{itemize}

### 2023-09-21 paper.tex
Mario's update (before class)

@@
 We finalize with a statistical Z-Test with a ninety-five percent confidence level to determine the best alternative.
-Table~\ref{tab.benchmark_functions} lists the thirty mathematical benchmark functions used for evaluation, to obtain the comparison results shown in our research.
+These benchmark functions include shifted and rotated versions of traditional benchmark functions (F1-F10), furthermore, there are ten hybrid versions combining the previous functions (F11-F20).
+The last functions (F21-30) include several compositions of previous benchmark functions, these are the most difficult variants.
 
@@
     We describe how to interpret the results presented in our Box and Whisker charts for each mathematical function.
-We display the ten and thirty-dimension charts on the left and right sides.
-We can find the results accumulated in 51 runs, in green color the One Point crossover, and in blue color the Continuous Range crossover.
-The closer the error results get to the zero value, the better.
+For these experiments, we choose to test the benchmark functions with ten and thirty dimensions, while there are higher dimensions, these two present enough challenges to the algorithms to compare the search performance in this kind of problem.
+According to the rules of the CEC 2017 Benchmark, the number of runs must be 51.
+The results in the table are then the box plot showing the median of the 51 runs.
+In green color, we show the results of the canonical One Point crossover found in the original version of GAs, on the right side, in blue color we show the results of our current proposal, the Continuous Range crossover.
+Because the goal is to minimize the functions, the closer the error values are to the zero value, the better.
 Below, we describe Figure~\ref{fig.experiment_F1-F5}, which includes Functions 1 to 5 (F1 to F5).
+In function F1 for the 10-dimension difficulty, the Continuous Range Crossover (CRx) methodology outperformed the One Point Crossover (OPx) methodology in the statistical test.
+On the other hand, we needed to find more evidence for thirty dimensions to determine whether any crossover alternative would be better.
+In the F2 function, for 10 dimensions, again, our proposed approach outperformed the OPx.
+Moreover, for function F3 for both dimensions, the statistical test found better results for our proposed CRx strategy.
+At function F4, only for the 10-dimensional problem, the CRx strategy turned out to be better through the statistical test, while for 30 dimensions, there was not a statistically clear winner.
+Finally, for F5, the statistical test passed only in 10 dimensions.
 
-    \begin{itemize}
-        \item In function F1 for the ten-dimensional category, the Continuous Range Crossover (CRx) methodology outperformed the One Point Crossover (OPx) methodology in the statistical test.
-We needed to find more evidence for the thirty dimensions category to determine whether any crossover alternative would be better.
-        \item At function F2 for the category of 10 dimensions, again, the CRx strategy outperformed the alternative approach OPx in the statistical test.
-More evidence was required for the thirty dimensions category to declare any of them as the best.
-        \item At function F3 for both categories, 10 and 30 dimensions, the statistical test found better results for our proposed CRx strategy than the alternative OPx.
-        \item At function F4, only for the 10-dimensional category, the CRx strategy proved to be better through the statistical test, while for the 30-dimensional variety, it could not identify any of them as the best.
-        \item At function F5, only for the 10-dimensional category, the proposed strategy CRx passed the statistical test compared to its alternative OPx, while for the 30-dimensional type, they obtained similar results.
-    \end{itemize}
-
-    We describe the results shown in Figure~\ref{fig.experiment_F6-F10}, including functions F6 through F10.
+    We now describe the results for the next set of functions shown in Figure~\ref{fig.experiment_F6-F10}, including functions F6 through F10.
 

### 2023-09-21 paper.tex
Functions F1-F20 description update.

@@
 Because the goal is to minimize the functions, the closer the error values are to the zero value, the better.
-Below, we describe Figure~\ref{fig.experiment_F1-F5}, which includes Functions 1 to 5 (F1 to F5).
+Below, we describe Figure~\ref{fig.experiment_F1-F5}, which includes functions F1 to F5.
 In function F1 for the 10-dimension difficulty, the Continuous Range Crossover (CRx) methodology outperformed the One Point Crossover (OPx) methodology in the statistical test.
@@
     We now describe the results for the next set of functions shown in Figure~\ref{fig.experiment_F6-F10}, including functions F6 through F10.
+In function F6, only for the 30-dimension difficulty, the canonical OPx alternative surpassed our proposal in the statistical test for the first occasion.
+On the following function, F7, only for the 10-dimension, our proposed CRx outperforms its alternative through the statistical test.
+Moreover, for functions F8 and F9 for both dimensions, the statistical test found better results for our proposed CRx strategy.
+For the function F10, the opposite of the previous function occurred, where for both dimensions, the classic OPx strategy obtained better results than our proposal.
+We describe the results in Figure~\ref{fig.experiment_F11-F15}, including functions F11 through F15.
+At function F11, only for the 10-dimension, the original OPx passed the statistical test compared to our proposed strategy.
+For function F12, the CRx strategy found better results for both tested dimensions than the canonical alternative, passing the statistical test.
+Our proposed strategy proved a better alternative for the F13, F14, and F15 functions at the 30 dimensions test run.
+We continue describing the results shown in Figure~\ref{fig.experiment_F16-F20}, which includes functions F16 to F20.
+At function F16, both alternatives obtained similar results on both tested dimensions.
+While for function F17 only for the 10-dimension, our proposed strategy proved better.
+On the other hand, at functions F18 and F19, only at the 30-dimension test, our proposed CRx passed the statistical test.
+Finally, for function F20, both crossover alternatives tested equivalent results.
 
-    \begin{itemize}
-        \item In function F6, for the category of 10 dimensions, there needed to be more evidence to determine that any of the proposals were best.
-For the variety of 30, the OPx alternative surpassed our CRx proposal in the statistical test for the first occasion.
-        \item At function F7, for the category of 10 dimensions, once again, the CRx strategy outperforms its alternative through the statistical test.
-For the 30-dimension type, we found not enough evidence to declare any of them as the best proposal.
-        \item At function F8, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
-        \item At function F9, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
-        \item At function F10, the opposite of the previous function occurred, where for both dimensions, 10 and 30, the classic OPx strategy obtained better results than our CRx proposal by passing the statistical test in both cases.
-    \end{itemize}
+    We continue with the description for the following set of functions shown in Figure~\ref{fig.experiment_F21-F25}, which includes functions f21 through F25.
 
-    We describe the results shown in Figure~\ref{fig.experiment_F11-F15}, including functions F11 through F15.
-
-    \begin{itemize}
-        \item At function F11, only for the 10-dimensional category, the original OPx passed the statistical test compared to our proposed strategy CRx, while for the 30-dimensional type, they obtained similar results.
-        \item At function F12, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
-
-    \end{itemize}
+    We finalize with the description for our last set of functions shown in Figure~\ref{fig.experiment_F26-F30}, which includes functions f26 through F30.
 

### 2023-09-22 paper.tex
Afternoon update.

@@
 We expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals.
-This paper uses the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC2017) to compare the traditional one-point crossover and our proposed strategy.
+This paper uses the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) to compare the traditional one-point crossover and our proposed strategy.
 Experimental results indicate that our proposed operator may be a good alternative for the canonical crossover.}
@@
 We expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals.
-In this paper, we use the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC2017) to compare the traditional one-point crossover and our proposed strategy.
+In this paper, we use the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) to compare the traditional one-point crossover and our proposed strategy.
 Experimental results indicate that our proposed operator may be a good alternative for the canonical crossover.}
@@
     We propose a new reproduction alternative in this research: a new breeding crossover approach for evolutionary algorithms using the classic one-point crossover as a reference to our proposal.
-We performed comparison experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) for evaluation.
+We performed comparison experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation\cite{awad2016problem} for the 2017 edition (CEC-2017) for evaluation.
 We finalize with a statistical Z-Test with a ninety-five percent confidence level to determine the best alternative.
@@
 This strategy is practical in evolutionary algorithms where the individual's information has a structure similar to the genetic code's.
-With some tinkering, this strategy could be valuable in other algorithms\cite{venter2003particle,wang2018particle}, such as Particle Swarm Optimization (PSO).
+With some tinkering, this strategy could be valuable in other algorithms\cite{venter2003particle,wang2018particle,mcdevitt2022particle}, such as Particle Swarm Optimization (PSO).
 
@@
 
-    To validate our proposal, we performed experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) for evaluation to compare the traditional one-point crossover and our proposed strategy.
+    To validate our proposal, we performed experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation\cite{awad2016problem} for the 2017 edition (CEC-2017) for evaluation to compare the traditional one-point crossover and our proposed strategy.
 We finalize with a statistical Z-Test with a ninety-five percent confidence level to determine the best alternative.
@@
 
-    \begin{table}[]
-    \scriptsize
-    \centering
-    \caption{Mathematical benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017).}\label{tab.benchmark_functions}    
-    \begin{tabular}{@{}cllcl@{}}
-    \toprule
-    \multicolumn{5}{c}{\textbf{CEC-2017 Mathematical Benchmark Functions}} \\ \midrule
-    \textbf{Fx} & \textbf{Function Name} &  & \textbf{Fx} & \textbf{Function Name} \\
-    F1 & Shifted and Rotated   Bent Cigar Function &  & F16 & Hybrid function 6 \\
-    F2 & Shifted and Rotated   Sum of Different Power Function &  & F17 & Hybrid function 7 \\
-    F3 & Shifted and Rotated   Zakharov Function &  & F18 & Hybrid function 8 \\
-    F4 & Shifted and Rotated   Rosenbrock's Function &  & F19 & Hybrid function 9 \\
-    F5 & Shifted and Rotated   Rastrigin's Function &  & F20 & Hybrid function 10 \\
-    F6 & Shifted and Rotated   Schaffer F7 Function &  & F21 & Composition function   1 \\
-    F7 & Shifted and Rotated   Lunacek Bi-Rastrigin's Function &  & F22 & Composition function   2 \\
-    F8 & Shifted and Rotated   Non-Continuous Rastrigin's Function &  & F23 & Composition function   3 \\
-    F9 & Shifted and Rotated   Levy Function &  & F24 & Composition function   4 \\
-    F10 & Shifted and Rotated   Schwefel's Function &  & F25 & Composition function   5 \\
-    F11 & Hybrid function 1 &  & F26 & Composition function   6 \\
-    F12 & Hybrid function 2 &  & F27 & Composition function   7 \\
-    F13 & Hybrid function 3 &  & F28 & Composition function   8 \\
-    F14 & Hybrid function 4 &  & F29 & Composition function   9 \\
-    F15 & Hybrid function 5 &  & F30 & Composition function   10 \\ \bottomrule
-    \end{tabular}
-    \end{table}
+    We can find a detailed description of the CEC-2017 mathematical benchmark functions, their equations, graphs, and classification in the document \textit{"Problem Definitions and Evaluation Criteria for the CEC 2017 Special Session and Competition on Single Objective Real-Parameter Numerical Optimization"} \cite{awad2016problem}.
 

### 2023-09-22 paper.tex
Afternoon Updates.

@@
         \includegraphics[width=0.90\linewidth]{img/fig_algorithm_model.pdf}
-        \caption{Animal Life Cycle Algorithm model\cite{Felix-Saul2023}.} \label{fig.algorithm_model}
+        \caption{General model concept for the Animal Life Cycle Algorithm (ALCA)\cite{Felix-Saul2023}.} \label{fig.algorithm_model}
         \end{figure}
@@
     \multicolumn{2}{l}{\textbf{ALCA   General Configuration}} \\ \midrule
-    \textbf{Function name} & \textbf{ALL} \\
-    Population & 500 \\
-    Evaluations & 10,000 * Dim \\
-    Crossover rate & 100 \\
-    Mutation rate & 7 \\
-    Max age & 5 \\
-    Tournament rep. & 100 \\
-    Sample size & 20 \\
-    Base approval & 80 \\
-    Goal approval & 200 \\ \bottomrule
+    \textbf{Dimensions Evaluated} & \textbf{10, 30} \\
+    Population' Individuals & 500 \\
+    Maximum Evaluations & 10,000 * Dim \\
+    Rate for Crossover & 100 \\
+    Rate for Mutation & 7 \\
+    Maximum Age & 5 \\
+    Rate for Tournament & 100 \\
+    Size of Sample & 20 \\
+    Minimum Approval & 80 \\
+    Maximum Approval & 200 \\ \bottomrule
     \end{tabular}

### 2023-09-22 paper.tex
Late night update.

@@
 We continue describing the results shown in Figure~\ref{fig.experiment_F16-F20}, which includes functions F16 to F20.
-At function F16, both alternatives obtained similar results on both tested dimensions.
+At function F16, both alternatives obtained similar results on tested dimensions.
 While for function F17 only for the 10-dimension, our proposed strategy proved better.
@@
 
-    We continue with the description for the following set of functions shown in Figure~\ref{fig.experiment_F21-F25}, which includes functions f21 through F25.
+    We continue with the description for the following set of functions shown in Figure~\ref{fig.experiment_F21-F25}, which includes functions F21 through F25.
+Results obtained at F21 show that only at 30 dimensions did our proposed strategy prove statistically better.
+Where at F22 on the 10-dimension, the original OPx was the best, for the 30-dimension, our proposed CRx was declared the winner.
+On the next F23, the OPx proved better for both tested dimensions.
+At function F24, on the lower 10-dimension, the CRx was a clear victor, while at the 30-dimension, the original OPx was the most precise.
+The canonical strategy was the most suitable alternative for the last test operation, F25, only at the 30-dimension.
 

### 2023-09-22 paper.tex
Late night update.

@@
 The canonical strategy was the most suitable alternative for the last test operation, F25, only at the 30-dimension.
-
-    We finalize with the description for our last set of functions shown in Figure~\ref{fig.experiment_F26-F30}, which includes functions f26 through F30.
+We finalize with the description for our last set of functions shown in Figure~\ref{fig.experiment_F26-F30}, which includes functions F26 through F30.
+The statistical test found no clear winner for the crossover alternatives at the mathematical evaluations, F26, F27, and F29.
+On the other hand, at operation F28, the proposed CRx statistically overcomes the canonical strategy for both tested dimensions.
+Lastly, at F30, our proposed CRx was the best alternative for the 30-dimension test.
 

### 2023-09-22 paper.tex
Final Update (Turnitin ready)
Condensed Tables Update

@@
 Lastly, at F30, our proposed CRx was the best alternative for the 30-dimension test.
+
+\section{Discussion}
+    \label{section.discussion}
+
+    For our experimentation, we executed fifty-one independent runs per specified dimension for each CEC-2017 mathematical benchmark function.
+We registered the following values: best-found error average and standard deviation to calculate the statistical Z-Test value.
+We summarized our results in the following tables, with the labels described next:
+
+    \begin{itemize}
+        \item   Fx:          is the mathematical benchmark function.
+        \item   Mean:        is the average of the best-found error.
+        \item   St-Dev:      is the computed error standard deviation. 
+        \item   Z:           is the calculated statistical Z-Test value.
+    \end{itemize}
+
+    To find and determine the best alternative, finalized with a statistical Z-Test with a ninety-five percent confidence level.
+Here are the results' statistics values: Table~\ref{tab.condensed_evaluation_10D} shows the condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions (D) for alternatives One Point and Continuous Range crossover; Table~\ref{tab.condensed_evaluation_30D} displays the condensed ALCA evaluation results for the CEC-2017 mathematical operations running on thirty D for the same crossover alternatives.
+
+    \begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions for alternatives One Point and Continuous Range crossover.}\label{tab.condensed_evaluation_10D}    
+    \begin{tabular}{@{}cllllllll@{}}
+    \toprule
+    \multicolumn{9}{c}{\textbf{ALCA   . CEC-2017 Benchmark Functions . 10 Dim}} \\ \midrule
+    \textbf{Crossover} & \textbf{} & \multicolumn{3}{c}{\textbf{One Point   Xover}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{3}{c}{\textbf{Cont. Range   Xover}} \\
+    Fx &  & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Std.
+Dev.} & \multicolumn{1}{c}{Z} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Std.
+Dev.} & \multicolumn{1}{c}{Z} \\
+    F1 &  & 2.1389E+03 & 2.1399E+03 & 5.4192E+00 &  & 4.4273E+02 & 6.4605E+02 & \textbf{-5.4192E+00} \\
+    F2 &  & 1.8100E-03 & 2.6299E-03 & 2.3752E+00 &  & 8.5385E-04 & 1.1614E-03 & \textbf{-2.3752E+00} \\
+    F3 &  & 4.1859E-04 & 1.1643E-03 & 2.4856E+00 &  & 1.3284E-05 & 2.1996E-05 & \textbf{-2.4856E+00} \\
+    F4 &  & 6.0009E+00 & 1.3061E+01 & 1.9980E+00 &  & 2.3131E+00 & 1.7796E+00 & \textbf{-1.9980E+00} \\
+    F5 &  & 1.5256E+01 & 7.0569E+00 & 2.4517E+00 &  & 1.2447E+01 & 4.1425E+00 & \textbf{-2.4517E+00} \\
+    F6 &  & 6.0531E-04 & 9.2170E-04 & -1.4267E+00 &  & 2.5341E-03 & 9.6104E-03 & 1.4267E+00 \\
+    F7 &  & 3.1484E+01 & 9.0577E+00 & 2.2567E+00 &  & 2.7585E+01 & 8.3786E+00 & \textbf{-2.2567E+00} \\
+    F8 &  & 1.7792E+01 & 7.3832E+00 & 8.0015E+00 &  & 8.6230E+00 & 3.5299E+00 & \textbf{-8.0015E+00} \\
+    F9 &  & 2.0213E+01 & 2.2424E+01 & 1.8477E+00 &  & 1.2506E+01 & 1.9608E+01 & \textbf{-1.8477E+00} \\
+    F10 &  & 4.9585E+02 & 2.2558E+02 & \textbf{-2.0236E+00} &  & 5.9412E+02 & 2.6338E+02 & 2.0236E+00 \\
+    F11 &  & 1.1599E+01 & 6.0084E+00 & \textbf{-2.4372E+00} &  & 1.4872E+01 & 7.4763E+00 & 2.4372E+00 \\
+    F12 &  & 1.6980E+04 & 1.9876E+04 & 1.9990E+00 &  & 1.0960E+04 & 8.2128E+03 & \textbf{-1.9990E+00} \\
+    F13 &  & 7.3909E+03 & 8.1574E+03 & 1.0784E+00 &  & 5.9436E+03 & 5.0303E+03 & -1.0784E+00 \\
+    F14 &  & 3.2387E+02 & 6.0517E+02 & 4.6471E-01 &  & 2.6685E+02 & 6.3381E+02 & -4.6471E-01 \\
+    F15 &  & 5.7005E+02 & 1.3121E+03 & 1.2452E+00 &  & 3.0689E+02 & 7.4575E+02 & -1.2452E+00 \\
+    F16 &  & 1.5553E+02 & 1.2806E+02 & 5.0519E-01 &  & 1.4323E+02 & 1.1771E+02 & -5.0519E-01 \\
+    F17 &  & 3.1678E+01 & 3.6537E+01 & 1.8131E+00 &  & 2.1124E+01 & 1.9819E+01 & \textbf{-1.8131E+00} \\
+    F18 &  & 2.2591E+03 & 2.8803E+03 & 9.0297E-01 &  & 1.7279E+03 & 3.0584E+03 & -9.0297E-01 \\
+    F19 &  & 1.8843E+03 & 3.2365E+03 & 4.1079E-01 &  & 1.6323E+03 & 2.9529E+03 & -4.1079E-01 \\
+    F20 &  & 9.5026E+00 & 8.3167E+00 & -1.3542E+00 &  & 1.1957E+01 & 9.9176E+00 & 1.3542E+00 \\
+    F21 &  & 1.1492E+02 & 3.8643E+01 & 4.9288E-02 &  & 1.1455E+02 & 3.5773E+01 & -4.9288E-02 \\
+    F22 &  & 1.0005E+02 & 2.0717E+01 & \textbf{-2.5672E+00} &  & 1.0813E+02 & 8.6974E+00 & 2.5672E+00 \\
+    F23 &  & 3.2068E+02 & 7.3128E+00 & \textbf{-2.5291E+00} &  & 3.2476E+02 & 8.9080E+00 & 2.5291E+00 \\
+    F24 &  & 3.2831E+02 & 8.0609E+01 & 5.3612E+00 &  & 2.1484E+02 & 1.2786E+02 & \textbf{-5.3612E+00} \\
+    F25 &  & 4.3486E+02 & 2.6137E+01 & 1.3872E+00 &  & 4.2795E+02 & 2.4061E+01 & -1.3872E+00 \\
+    F26 &  & 3.9878E+02 & 1.2472E+02 & 7.5476E-01 &  & 3.8231E+02 & 9.3517E+01 & -7.5476E-01 \\
+    F27 &  & 3.8835E+02 & 1.0299E+01 & -5.4299E-01 &  & 3.8951E+02 & 1.1293E+01 & 5.4299E-01 \\
+    F28 &  & 4.1119E+02 & 7.9226E+01 & 1.9297E+00 &  & 3.7987E+02 & 8.4606E+01 & \textbf{-1.9297E+00} \\
+    F29 &  & 2.9963E+02 & 4.3225E+01 & 7.4383E-01 &  & 2.9396E+02 & 3.3009E+01 & -7.4383E-01 \\
+    F30 &  & 3.2080E+02 & 1.5217E+02 & -7.1382E-01 &  & 3.4441E+02 & 1.8071E+02 & 7.1382E-01 \\
+    \textbf{Total   (W)} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{One Point   Xover}} & \multicolumn{1}{c}{\textbf{4 of 30}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Cont.
+Range   Xover}} & \multicolumn{1}{c}{\textbf{12 of 30}} \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+    \FloatBarrier
+
+    We performed the statistical Z-Test for both crossover alternatives with a 95 percent confidence level.
+When the One Point passes the test, the Z value is highlighted in bold on the left column.
+When the Continuous Range passes the statistical test, the Z value is highlighted in bold on the right column.
+Where we did not find enough evidence to declare one choice as the best alternative, no value was highlighted.
+
+    \begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Condensed ALCA evaluation results for the CEC-2017 functions running on thirty dimensions for alternatives One Point and Continuous Range crossover.}\label{tab.condensed_evaluation_30D}
+    \begin{tabular}{@{}cllllllll@{}}
+    \toprule
+    \multicolumn{9}{c}{\textbf{ALCA   . CEC-2017 Benchmark Functions . 30 Dim}} \\ \midrule
+    \textbf{Crossover} & \textbf{} & \multicolumn{3}{c}{\textbf{One Point   Xover}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{3}{c}{\textbf{Cont. Range   Xover}} \\
+    Fx &  & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Std.
+Dev.} & \multicolumn{1}{c}{Z} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Std.
+Dev.} & \multicolumn{1}{c}{Z} \\
+    F1 &  & 4.9221E+03 & 6.2052E+03 & 1.5981E+00 &  & 3.3461E+03 & 3.3306E+03 & -1.5981E+00 \\
+    F2 &  & 9.2072E+06 & 4.7678E+07 & 1.3686E+00 &  & 6.9569E+04 & 2.4985E+05 & -1.3686E+00 \\
+    F3 &  & 1.1683E+02 & 1.1804E+02 & 4.3284E+00 &  & 4.1582E+01 & 3.8455E+01 & \textbf{-4.3284E+00} \\
+    F4 &  & 7.1658E+01 & 3.1444E+01 & -5.2921E-01 &  & 7.4645E+01 & 2.5202E+01 & 5.2921E-01 \\
+    F5 &  & 9.3827E+01 & 2.4093E+01 & 4.6068E-01 &  & 9.1790E+01 & 2.0430E+01 & -4.6068E-01 \\
+    F6 &  & 4.6723E-03 & 1.0247E-02 & \textbf{-2.4217E+00} &  & 2.2849E-02 & 5.2614E-02 & 2.4217E+00 \\
+    F7 &  & 1.5523E+02 & 3.0419E+01 & -3.8825E-01 &  & 1.5772E+02 & 3.4361E+01 & 3.8825E-01 \\
+    F8 &  & 9.9361E+01 & 2.4339E+01 & 6.8232E+00 &  & 7.2924E+01 & 1.3162E+01 & \textbf{-6.8232E+00} \\
+    F9 &  & 1.3710E+03 & 7.2076E+02 & 4.6028E+00 &  & 8.1853E+02 & 4.6408E+02 & \textbf{-4.6028E+00} \\
+    F10 &  & 2.7912E+03 & 5.5872E+02 & \textbf{-2.2216E+00} &  & 3.0169E+03 & 4.6303E+02 & 2.2216E+00 \\
+    F11 &  & 7.3052E+01 & 2.7205E+01 & -1.0895E+00 &  & 7.8958E+01 & 2.7541E+01 & 1.0895E+00 \\
+    F12 &  & 2.1831E+05 & 1.9392E+05 & 4.6137E+00 &  & 8.7259E+04 & 5.9525E+04 & \textbf{-4.6137E+00} \\
+    F13 &  & 1.9452E+04 & 2.7290E+04 & 2.0901E+00 &  & 1.1046E+04 & 8.9591E+03 & \textbf{-2.0901E+00} \\
+    F14 &  & 2.2151E+04 & 2.1428E+04 & 2.8255E+00 &  & 1.2691E+04 & 1.0610E+04 & \textbf{-2.8255E+00} \\
+    F15 &  & 1.2499E+04 & 1.4069E+04 & 4.9618E+00 &  & 2.3697E+03 & 3.8202E+03 & \textbf{-4.9618E+00} \\
+    F16 &  & 1.2641E+03 & 3.4529E+02 & 1.4923E-01 &  & 1.2552E+03 & 2.4941E+02 & -1.4923E-01 \\
+    F17 &  & 6.0224E+02 & 1.7565E+02 & 1.1651E+00 &  & 5.5424E+02 & 2.3605E+02 & -1.1651E+00 \\
+    F18 &  & 1.2865E+05 & 1.1706E+05 & 2.9170E+00 &  & 7.4398E+04 & 6.2747E+04 & \textbf{-2.9170E+00} \\
+    F19 &  & 9.7805E+03 & 1.1607E+04 & 3.0408E+00 &  & 4.3849E+03 & 5.0850E+03 & \textbf{-3.0408E+00} \\
+    F20 &  & 4.8317E+02 & 1.6940E+02 & 1.0238E-01 &  & 4.7938E+02 & 2.0307E+02 & -1.0238E-01 \\
+    F21 &  & 3.0294E+02 & 2.4353E+01 & 4.3999E+00 &  & 2.8493E+02 & 1.6184E+01 & \textbf{-4.3999E+00} \\
+    F22 &  & 1.7571E+03 & 1.7169E+03 & 6.0688E+00 &  & 2.1583E+02 & 5.8436E+02 & \textbf{-6.0688E+00} \\
+    F23 &  & 4.6160E+02 & 3.0564E+01 & \textbf{-5.2747E+00} &  & 5.0468E+02 & 4.9672E+01 & 5.2747E+00 \\
+    F24 &  & 6.4513E+02 & 7.4299E+01 & \textbf{-2.3148E+00} &  & 6.7829E+02 & 7.0328E+01 & 2.3148E+00 \\
+    F25 &  & 3.8492E+02 & 1.4918E+01 & \textbf{-3.0635E+00} &  & 3.9704E+02 & 2.3987E+01 & 3.0635E+00 \\
+    F26 &  & 2.3955E+03 & 4.8813E+02 & -1.2340E+00 &  & 2.6143E+03 & 1.1683E+03 & 1.2340E+00 \\
+    F27 &  & 4.9415E+02 & 1.2280E+01 & 2.9755E-01 &  & 4.9319E+02 & 1.9531E+01 & -2.9755E-01 \\
+    F28 &  & 4.6268E+02 & 4.2897E+01 & 9.2609E+00 &  & 3.9779E+02 & 2.5756E+01 & \textbf{-9.2609E+00} \\
+    F29 &  & 9.2249E+02 & 2.3560E+02 & 1.5461E+00 &  & 8.5552E+02 & 2.0043E+02 & -1.5461E+00 \\
+    F30 &  & 3.5332E+03 & 4.1540E+03 & 4.0881E+00 &  & 1.0823E+03 & 1.0372E+03 & \textbf{-4.0881E+00} \\
+    \textbf{Total   (W)} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{One Point   Xover}} & \multicolumn{1}{c}{\textbf{5 of 30}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Cont.
+Range   Xover}} & \multicolumn{1}{c}{\textbf{13 of 30}} \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+    \FloatBarrier
+
+\section{Conclusions}
+    \label{section.conclusions}
+
+    To validate our research, we performed the statistical Z-Test with a ninety-five percent confidence level to analyze the alternatives we present in this proposal.
+In the ten-dimension category, we found that One Point crossover was the better alternative on four occasions, while our Continuous Range proposal was better on twelve other functions out of thirty.
+For the thirty-dimensions category, the One Point crossover was better on five occasions, while the Continuous Range crossover was the best alternative on another thirteen.
+Our experiment results confirm that our solution can be considered an adequate alternative.
+
+    Some researchers might consider our proposal similar to what is used by algorithms such as Differential Evolution, where we consider our proposal to be a variation of existing proposals because we expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals.
+Experimental results indicate that our proposed operator may be a viable alternative for the canonical One Point crossover.
+
+    Based on the analysis of our results, we have shown that the proposed crossover alternative for the reproduction of individuals in a population obtains good results.
+Therefore, it can be valuable in other evolutionary algorithms where the information of individuals has a structure similar to that of the genetic code.
+However, with some adaptation, it could be helpful in different types of algorithms, such as Particle Swarm Optimization.
+In future work, we could investigate a combination between the canonical One Point Crossover strategy and randomly alternating with the proposed Continuous Range Crossover.
+
+\begin{acknowledgement}
+    TecNM Project 18186.23-P has partially funded this research.
+\end{acknowledgement}
 
@@
 
-\section{Discussion}
-    \label{section.discussion}
-
-    For our experimentation, we executed fifty-one independent runs per specified dimension for each CEC-2017 mathematical benchmark function.
-We registered the following values: best-found error average and standard deviation to calculate the statistical Z-Test value.
-We summarized our results in the following tables, with the labels described next:
-
-    \begin{itemize}
-        \item   Fx:          is the mathematical benchmark function.
-        \item   Mean:        is the average of the best-found error.
-        \item   St-Dev:      is the computed error standard deviation. 
-        \item   Z:           is the calculated statistical Z-Test value.
-    \end{itemize}
-
-    To find and determine the best alternative, finalized with a statistical Z-Test with a ninety-five percent confidence level.
-Here are the results' statistics values: Table~\ref{tab.condensed_evaluation_10D} shows the condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions (D) for alternatives One Point and Continuous Range crossover; Table~\ref{tab.condensed_evaluation_30D} displays the condensed ALCA evaluation results for the CEC-2017 mathematical operations running on thirty D for the same crossover alternatives.
-
-    \begin{table}[]
-    \scriptsize
-    \centering
-    \caption{Condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions for alternatives One Point and Continuous Range crossover.}\label{tab.condensed_evaluation_10D}
-    \begin{tabular}{@{}lllllllll@{}}
-    \toprule
-    \multicolumn{9}{c}{\textbf{ALCA . CEC-2017 . 10D}} \\ \midrule
-    Crossover &  & \multicolumn{3}{c}{One Point Xover} &  & \multicolumn{3}{c}{Cont. Range Xover} \\
-    Fx &  & Mean & Std. Dev. & Z &  & Mean & Std. Dev. & Z \\
-    F1 &  & 2.14E+03 & 2.14E+03 & 5.42E+00 &  & 4.43E+02 & 6.46E+02 & \textbf{-5.42E+00} \\
-    F2 &  & 1.81E-03 & 2.63E-03 & 2.38E+00 &  & 8.54E-04 & 1.16E-03 & \textbf{-2.38E+00} \\
-    F3 &  & 4.19E-04 & 1.16E-03 & 2.49E+00 &  & 1.33E-05 & 2.20E-05 & \textbf{-2.49E+00} \\
-    F4 &  & 6.00E+00 & 1.31E+01 & 2.00E+00 &  & 2.31E+00 & 1.78E+00 & \textbf{-2.00E+00} \\
-    F5 &  & 1.53E+01 & 7.06E+00 & 2.45E+00 &  & 1.24E+01 & 4.14E+00 & \textbf{-2.45E+00} \\
-    F6 &  & 6.05E-04 & 9.22E-04 & -1.43E+00 &  & 2.53E-03 & 9.61E-03 & 1.43E+00 \\
-    F7 &  & 3.15E+01 & 9.06E+00 & 2.26E+00 &  & 2.76E+01 & 8.38E+00 & \textbf{-2.26E+00} \\
-    F8 &  & 1.78E+01 & 7.38E+00 & 8.00E+00 &  & 8.62E+00 & 3.53E+00 & \textbf{-8.00E+00} \\
-    F9 &  & 2.02E+01 & 2.24E+01 & 1.85E+00 &  & 1.25E+01 & 1.96E+01 & \textbf{-1.85E+00} \\
-    F10 &  & 4.96E+02 & 2.26E+02 & \textbf{-2.02E+00} &  & 5.94E+02 & 2.63E+02 & 2.02E+00 \\
-    F11 &  & 1.16E+01 & 6.01E+00 & \textbf{-2.44E+00} &  & 1.49E+01 & 7.48E+00 & 2.44E+00 \\
-    F12 &  & 1.70E+04 & 1.99E+04 & 2.00E+00 &  & 1.10E+04 & 8.21E+03 & \textbf{-2.00E+00} \\
-    F13 &  & 7.39E+03 & 8.16E+03 & 1.08E+00 &  & 5.94E+03 & 5.03E+03 & -1.08E+00 \\
-    F14 &  & 3.24E+02 & 6.05E+02 & 4.65E-01 &  & 2.67E+02 & 6.34E+02 & -4.65E-01 \\
-    F15 &  & 5.70E+02 & 1.31E+03 & 1.25E+00 &  & 3.07E+02 & 7.46E+02 & -1.25E+00 \\
-    F16 &  & 1.56E+02 & 1.28E+02 & 5.05E-01 &  & 1.43E+02 & 1.18E+02 & -5.05E-01 \\
-    F17 &  & 3.17E+01 & 3.65E+01 & 1.81E+00 &  & 2.11E+01 & 1.98E+01 & \textbf{-1.81E+00} \\
-    F18 &  & 2.26E+03 & 2.88E+03 & 9.03E-01 &  & 1.73E+03 & 3.06E+03 & -9.03E-01 \\
-    F19 &  & 1.88E+03 & 3.24E+03 & 4.11E-01 &  & 1.63E+03 & 2.95E+03 & -4.11E-01 \\
-    F20 &  & 9.50E+00 & 8.32E+00 & -1.35E+00 &  & 1.20E+01 & 9.92E+00 & 1.35E+00 \\
-    F21 &  & 1.15E+02 & 3.86E+01 & 4.93E-02 &  & 1.15E+02 & 3.58E+01 & -4.93E-02 \\
-    F22 &  & 1.00E+02 & 2.07E+01 & \textbf{-2.57E+00} &  & 1.08E+02 & 8.70E+00 & 2.57E+00 \\
-    F23 &  & 3.21E+02 & 7.31E+00 & \textbf{-2.53E+00} &  & 3.25E+02 & 8.91E+00 & 2.53E+00 \\
-    F24 &  & 3.28E+02 & 8.06E+01 & 5.36E+00 &  & 2.15E+02 & 1.28E+02 & \textbf{-5.36E+00} \\
-    F25 &  & 4.35E+02 & 2.61E+01 & 1.39E+00 &  & 4.28E+02 & 2.41E+01 & -1.39E+00 \\
-    F26 &  & 3.99E+02 & 1.25E+02 & 7.55E-01 &  & 3.82E+02 & 9.35E+01 & -7.55E-01 \\
-    F27 &  & 3.88E+02 & 1.03E+01 & -5.43E-01 &  & 3.90E+02 & 1.13E+01 & 5.43E-01 \\
-    F28 &  & 4.11E+02 & 7.92E+01 & 1.93E+00 &  & 3.80E+02 & 8.46E+01 & \textbf{-1.93E+00} \\
-    F29 &  & 3.00E+02 & 4.32E+01 & 7.44E-01 &  & 2.94E+02 & 3.30E+01 & -7.44E-01 \\
-    F30 &  & 3.21E+02 & 1.52E+02 & -7.14E-01 &  & 3.44E+02 & 1.81E+02 & 7.14E-01 \\
-    \textbf{Total (W)} &  & \multicolumn{2}{c}{\textbf{One Point Xover}} & \multicolumn{1}{c}{\textbf{4 of 30}} &  & \multicolumn{2}{c}{\textbf{Cont.
-Range Xover}} & \multicolumn{1}{c}{\textbf{12 of 30}} \\ \bottomrule
-    \end{tabular}
-    \end{table}
-
-    \FloatBarrier
-
-    We performed the statistical Z-Test for both crossover alternatives with a 95 percent confidence level.
-When the One Point passes the test, the Z value is highlighted in bold on the left column.
-When the Continuous Range passes the statistical test, the Z value is highlighted in bold on the right column.
-Where we did not find enough evidence to declare one choice as the best alternative, no value was highlighted.
-
-    \begin{table}[]
-    \scriptsize
-    \centering
-    \caption{Condensed ALCA evaluation results for the CEC-2017 functions running on thirty dimensions for alternatives One Point and Continuous Range crossover.}\label{tab.condensed_evaluation_30D}
-    \begin{tabular}{@{}lllllllll@{}}
-    \toprule
-    \multicolumn{9}{c}{\textbf{ALCA . CEC-2017 . 30D}} \\ \midrule
-    Crossover &  & \multicolumn{3}{c}{One Point Xover} &  & \multicolumn{3}{c}{Cont. Range Xover} \\
-    Fx &  & Mean & Std. Dev. & Z &  & Mean & Std. Dev. & Z \\
-    F1 &  & 4.92E+03 & 6.21E+03 & 1.60E+00 &  & 3.35E+03 & 3.33E+03 & -1.60E+00 \\
-    F2 &  & 9.21E+06 & 4.77E+07 & 1.37E+00 &  & 6.96E+04 & 2.50E+05 & -1.37E+00 \\
-    F3 &  & 1.17E+02 & 1.18E+02 & 4.33E+00 &  & 4.16E+01 & 3.85E+01 & \textbf{-4.33E+00} \\
-    F4 &  & 7.17E+01 & 3.14E+01 & -5.29E-01 &  & 7.46E+01 & 2.52E+01 & 5.29E-01 \\
-    F5 &  & 9.38E+01 & 2.41E+01 & 4.61E-01 &  & 9.18E+01 & 2.04E+01 & -4.61E-01 \\
-    F6 &  & 4.67E-03 & 1.02E-02 & \textbf{-2.42E+00} &  & 2.28E-02 & 5.26E-02 & 2.42E+00 \\
-    F7 &  & 1.55E+02 & 3.04E+01 & -3.88E-01 &  & 1.58E+02 & 3.44E+01 & 3.88E-01 \\
-    F8 &  & 9.94E+01 & 2.43E+01 & 6.82E+00 &  & 7.29E+01 & 1.32E+01 & \textbf{-6.82E+00} \\
-    F9 &  & 1.37E+03 & 7.21E+02 & 4.60E+00 &  & 8.19E+02 & 4.64E+02 & \textbf{-4.60E+00} \\
-    F10 &  & 2.79E+03 & 5.59E+02 & \textbf{-2.22E+00} &  & 3.02E+03 & 4.63E+02 & 2.22E+00 \\
-    F11 &  & 7.31E+01 & 2.72E+01 & -1.09E+00 &  & 7.90E+01 & 2.75E+01 & 1.09E+00 \\
-    F12 &  & 2.18E+05 & 1.94E+05 & 4.61E+00 &  & 8.73E+04 & 5.95E+04 & \textbf{-4.61E+00} \\
-    F13 &  & 1.95E+04 & 2.73E+04 & 2.09E+00 &  & 1.10E+04 & 8.96E+03 & \textbf{-2.09E+00} \\
-    F14 &  & 2.22E+04 & 2.14E+04 & 2.83E+00 &  & 1.27E+04 & 1.06E+04 & \textbf{-2.83E+00} \\
-    F15 &  & 1.25E+04 & 1.41E+04 & 4.96E+00 &  & 2.37E+03 & 3.82E+03 & \textbf{-4.96E+00} \\
-    F16 &  & 1.26E+03 & 3.45E+02 & 1.49E-01 &  & 1.26E+03 & 2.49E+02 & -1.49E-01 \\
-    F17 &  & 6.02E+02 & 1.76E+02 & 1.17E+00 &  & 5.54E+02 & 2.36E+02 & -1.17E+00 \\
-    F18 &  & 1.29E+05 & 1.17E+05 & 2.92E+00 &  & 7.44E+04 & 6.27E+04 & \textbf{-2.92E+00} \\
-    F19 &  & 9.78E+03 & 1.16E+04 & 3.04E+00 &  & 4.38E+03 & 5.08E+03 & \textbf{-3.04E+00} \\
-    F20 &  & 4.83E+02 & 1.69E+02 & 1.02E-01 &  & 4.79E+02 & 2.03E+02 & -1.02E-01 \\
-    F21 &  & 3.03E+02 & 2.44E+01 & 4.40E+00 &  & 2.85E+02 & 1.62E+01 & \textbf{-4.40E+00} \\
-    F22 &  & 1.76E+03 & 1.72E+03 & 6.07E+00 &  & 2.16E+02 & 5.84E+02 & \textbf{-6.07E+00} \\
-    F23 &  & 4.62E+02 & 3.06E+01 & \textbf{-5.27E+00} &  & 5.05E+02 & 4.97E+01 & 5.27E+00 \\
-    F24 &  & 6.45E+02 & 7.43E+01 & \textbf{-2.31E+00} &  & 6.78E+02 & 7.03E+01 & 2.31E+00 \\
-    F25 &  & 3.85E+02 & 1.49E+01 & \textbf{-3.06E+00} &  & 3.97E+02 & 2.40E+01 & 3.06E+00 \\
-    F26 &  & 2.40E+03 & 4.88E+02 & -1.23E+00 &  & 2.61E+03 & 1.17E+03 & 1.23E+00 \\
-    F27 &  & 4.94E+02 & 1.23E+01 & 2.98E-01 &  & 4.93E+02 & 1.95E+01 & -2.98E-01 \\
-    F28 &  & 4.63E+02 & 4.29E+01 & 9.26E+00 &  & 3.98E+02 & 2.58E+01 & \textbf{-9.26E+00} \\
-    F29 &  & 9.22E+02 & 2.36E+02 & 1.55E+00 &  & 8.56E+02 & 2.00E+02 & -1.55E+00 \\
-    F30 &  & 3.53E+03 & 4.15E+03 & 4.09E+00 &  & 1.08E+03 & 1.04E+03 & \textbf{-4.09E+00} \\
-    \multicolumn{1}{c}{\textbf{Total (W)}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{One Point Xover}} & \multicolumn{1}{c}{\textbf{5 of 30}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Cont.
-Range Xover}} & \multicolumn{1}{c}{\textbf{13 of 30}} \\ \bottomrule
-    \end{tabular}
-    \end{table}
-
-    \FloatBarrier
-
-\section{Conclusions}
-    \label{section.conclusions}
-
-    To validate our research, we performed the statistical Z-Test with a ninety-five percent confidence level to analyze the alternatives we present in this proposal.
-In the ten-dimension category, we found that One Point crossover was the better alternative on four occasions, while our Continuous Range proposal was better on twelve other functions out of thirty.
-For the thirty-dimensions category, the One Point crossover was better on five occasions, while the Continuous Range crossover was the best alternative on another thirteen.
-Our experiment results confirm that our solution can be considered an adequate alternative.
-
-    Some researchers might consider our proposal similar to what is used by algorithms such as Differential Evolution, where we consider our proposal to be a variation of existing proposals because we expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals.
-Experimental results indicate that our proposed operator may be a viable alternative for the canonical One Point crossover.
-
-    Based on the analysis of our results, we have shown that the proposed crossover alternative for the reproduction of individuals in a population obtains good results.
-Therefore, it can be valuable in other evolutionary algorithms where the information of individuals has a structure similar to that of the genetic code.
-However, with some adaptation, it could be helpful in different types of algorithms, such as Particle Swarm Optimization.
-In future work, we could investigate a combination between the canonical One Point Crossover strategy and randomly alternating with the proposed Continuous Range Crossover.
-
-\begin{acknowledgement}
-    TecNM Project 18186.23-P has partially funded this research.
-\end{acknowledgement}
-
 % ---- Bibliography ----
